---
title: "Figures for: A machine learning interpretation of the contribution of foliar fungicides to soybean yield in the north‐central United States"
author: Denis Shah, Thomas Butts, Spyridon Mourtzinis, Juan Rattalino Edreira, Patricio Grassini, Shawn Conley and Paul Esker
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    fig_caption: yes
    highlight: tango
    number_sections: true
    theme: cerulean
    toc: yes
    toc_depth: 3
    toc_float: true
editor_options: 
  chunk_output_type: console  
---

----------------------------------------------------------------------------------------------------


```{r setup, include=FALSE, eval=TRUE}
require(knitr)
knitr::opts_chunk$set(cache=TRUE, fig.path = 'SoyFigs/')
```


<!--- Load libraries and process data for plotting -->
```{r libraries, echo=FALSE, eval=TRUE, message=FALSE}
library(tidyverse)
# tidyverse_packages(include_self = FALSE)
# Loads: dplyr forcats ggplot2 lubridate purrr tibble

# For producing maps:
library(sf)
# NOTE: sf requires maptools, rgeos to be loaded

# Random forest fitting and tuning
library(caret)
library(ranger)
library(tuneRanger)
library(mlr)

# Feature importance
library(iml)

# For color schemes:
library(RColorBrewer)
library(ggsci)

# For graphics layout:
library(gridExtra)
library(grid)
library(gtable)

library(kableExtra)

library(rcompanion)
```


<!--- Read in the management data -->
```{r MgmtData, eval=TRUE, echo=FALSE}
load("~/EskerSoybean/ScientificReportsGitHub/Data/Mgmt.RData")

dat <-
  dat %>%
  # Drop unused factor levels in state (i.e. SD):
  dplyr::mutate(state = droplevels(state)) %>%
  # Rename MG.f to MG:
  dplyr::rename(MG = MG.f) %>%
  # Convert yield from bu/acre to kg/ha (1 bushel/acre = 67.25 kg/ha, at 60 lb per bu):
  # dplyr::mutate(yield = yield*67.25) %>%
  # Convert yield from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
  dplyr::mutate(yield = yield*0.06725)

# For modeling drop: order, state, year, TED, longitude
datII <- dat %>% dplyr::select(-order, -state, -year, -TED, -longitude)

# Set up for mapping:
states <- sf::st_as_sf(maps::map("state", plot = FALSE, fill = TRUE))
# Subset to the states of interest:
soy2 <- states %>%
  subset(ID %in% c("iowa", "illinois", "indiana", "kansas", "michigan", "minnesota", "nebraska", "north dakota", "south dakota", "ohio", "wisconsin"))
```

# Summaries
```{r Summary-Stats, eval=FALSE, echo=FALSE}
# Proportion of fields treated with foliar fungicides:
dat %>% dplyr::group_by(foliar.fungicide) %>% dplyr::summarise(n= n())
# no = 1905, yes = 833 proportion sprayed = 833/2738 = 30.4%

# Proportion of fields treated with both foliar fungicides and insecticides:
dat %>% dplyr::group_by(foliar.fungicide, foliar.insecticide) %>% dplyr::summarise(n= n())

# Proportion by year:
dat %>% 
  dplyr::select(year, foliar.fungicide) %>%
  dplyr::group_by(year) %>%
  dplyr::summarise(n = n(), No = sum(foliar.fungicide == "no"), Yes = sum(foliar.fungicide == "yes"), prop.No = No/n, prop.Yes = Yes/n) %>%
  dplyr::ungroup() %>%
  dplyr::mutate_at(vars(prop.No, prop.Yes), round, digits = 3)

# Proportion by MG:
dat %>% 
  dplyr::select(MG, foliar.fungicide) %>%
  dplyr::group_by(MG) %>%
  dplyr::summarise(n = n(), No = sum(foliar.fungicide == "no"), Yes = sum(foliar.fungicide == "yes"), prop.No = No/n, prop.Yes = Yes/n) %>%
  dplyr::ungroup() %>%
  dplyr::mutate_at(vars(prop.No, prop.Yes), round, digits = 3)



## Estimate the mean yields for the sprayed and unsprayed cohorts of fields within the top 12 TEDs:
# The top 12 TEDs:
top.12.TEDs <- dat %>% dplyr::count(TED) %>% dplyr::arrange(-n) %>% dplyr::slice(1:12) %>% dplyr::pull(TED) 

# The number of fields for each of the two cohorts within the TEDs:
z1 <- 
dat %>%
  dplyr::filter(TED %in% top.12.TEDs) %>%
  dplyr::group_by(TED) %>%
  dplyr::summarise(n = n(), n.ff = sum(foliar.fungicide == "yes"), n.nff = sum(foliar.fungicide == "no")) %>%
  dplyr::arrange(desc(n))

# The mean yields for the sprayed cohorts:
z2 <-
dat %>%
  dplyr::filter(TED %in% top.12.TEDs) %>%
  dplyr::filter(foliar.fungicide == "yes") %>%
  dplyr::group_by(TED) %>%
  dplyr::summarise(ff.yld = mean(yield))

# The mean yields for the unsprayed cohorts:
z3 <- 
dat %>%
  dplyr::filter(TED %in% top.12.TEDs) %>%
  dplyr::filter(foliar.fungicide == "no") %>%
  dplyr::group_by(TED) %>%
  dplyr::summarise(nf.yld = mean(yield))

# Now combine the three data frames:
z <-
  list(z1, z2, z3) %>%
  purrr::reduce(dplyr::left_join, by = "TED")

# Sort by the mean yield for the sprayed fields:
z %>%
  dplyr::arrange(desc(ff.yld))

# Sort by the mean yield for the unsprayed fields:
z %>%
  dplyr::arrange(desc(nf.yld))

# For comparison, the global yield average:
mean(dat$yield)
```



# TEDs
```{r TEDs, eval=TRUE, echo=FALSE, results='hide'}
# 96 TEDs
dat %>% dplyr::count(TED)

# No. of fields in the top 12 TEDs:
dat %>% dplyr::count(TED) %>% dplyr::arrange(desc(n)) %>% dplyr::slice(1:12) %>% dplyr::tally(n)

# What percent is this out of all fields?
round(100*(dat %>% dplyr::count(TED) %>% dplyr::arrange(desc(n)) %>% dplyr::slice(1:12) %>% dplyr::tally(n))/nrow(dat), 1)
```


# Field locations {.tabset .tabset-fade .tabset-pills}
## By MG
<!-- Supplementary Figure S1 -->
```{r FieldLocations-MG, eval=TRUE, echo=FALSE}
# Locations of all the fields facetted by year, field locations colored by maturity group:
ggplot() +
  geom_sf(data = soy2) +
  theme_bw() +
  geom_point(data = dat, aes(x = longitude, y = latitude, colour = MG), size = 1.5, alpha = 0.5) +
  scale_color_brewer(type = "qual", palette = "Set1", direction = 1) +
  facet_wrap(~ year, ncol = 3) +
  xlab("Longitude") +
  ylab("Latitude") +
  theme(axis.title.x = element_text(face = "bold", size = 12),
        axis.text.x  = element_text(size = 9, angle = 90),
        axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
        axis.text.y  = element_text(size = 9),
        # Bold the facet text labels:
        strip.text = element_text(face = "bold", size = 10)) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "vertical") +
  # override the transparency of the points for the legend:
  guides(colour = guide_legend(nrow = 1, title = "Maturity group", override.aes = list(alpha = 1)))
```

## By PAWR
```{r FieldLocations-PAWR, eval=TRUE, echo=FALSE}
# Locations of all the fields facetted by year, field locations colored by PAWR:
ggplot() +
  geom_sf(data = soy2) +
  theme_bw() +
  geom_point(data = dat, aes(x = longitude, y = latitude, colour = PAWR), size = 1.0, alpha = 0.5) +
  scale_color_brewer(type = "qual", palette = "Set1", direction = 1) +
  facet_wrap(~ year, ncol = 3) +
  xlab("Longitude") +
  ylab("Latitude") +
  theme(axis.title.x = element_text(face = "bold", size = 12),
        axis.text.x  = element_text(size = 8, angle = 90),
        axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
        axis.text.y  = element_text(size = 8),
        # Bold the facet text labels:
        strip.text = element_text(face = "bold")) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "vertical") +
  # override the transparency of the points for the legend:
  guides(colour = guide_legend(nrow = 1, title = "PAWR", override.aes = list(alpha = 1)))
```

## By GDD
```{r FieldLocations-GDD, eval=TRUE, echo=FALSE}
# Locations of all the fields facetted by year, field locations colored by GDD:
ggplot() +
  geom_sf(data = soy2) +
  theme_bw() +
  geom_point(data = dat, aes(x = longitude, y = latitude, colour = GDD), size = 1.0, alpha = 0.5) +
  scale_color_brewer(type = "qual", palette = "Set1", direction = 1) +
  facet_wrap(~ year, ncol = 3) +
  xlab("Longitude") +
  ylab("Latitude") +
  theme(axis.title.x = element_text(face = "bold", size = 12),
        axis.text.x  = element_text(size = 8, angle = 90),
        axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
        axis.text.y  = element_text(size = 8),
        # Bold the facet text labels:
        strip.text = element_text(face = "bold")) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "vertical") +
  # override the transparency of the points for the legend:
  guides(colour = guide_legend(nrow = 1, title = "GDD", override.aes = list(alpha = 1)))
```


## By AI
```{r FieldLocations-AI, eval=TRUE, echo=FALSE}
# Locations of all the fields facetted by year, field locations colored by AI:
ggplot() +
  geom_sf(data = soy2) +
  theme_bw() +
  geom_point(data = dat, aes(x = longitude, y = latitude, colour = AI), size = 1.0, alpha = 0.5) +
  scale_color_brewer(type = "qual", palette = "Set1", direction = 1) +
  facet_wrap(~ year, ncol = 3) +
  xlab("Longitude") +
  ylab("Latitude") +
  theme(axis.title.x = element_text(face = "bold", size = 12),
        axis.text.x  = element_text(size = 8, angle = 90),
        axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
        axis.text.y  = element_text(size = 8),
        # Bold the facet text labels:
        strip.text = element_text(face = "bold")) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "vertical") +
  # override the transparency of the points for the legend:
  guides(colour = guide_legend(nrow = 1, title = "AI", override.aes = list(alpha = 1)))
```



# Random forest model fitting {.tabset .tabset-fade .tabset-pills}
## Tuning
```{r RFTuning, eval=FALSE, echo=FALSE}
# The RF algorithm assumes no missing data; there are no missing data in the data matrix being used.

# Set seed for reproducibility:
set.seed(14092)

# Create training & testing data sets:
# Use 0.80 split to avoid warnings about empty factor levels when mlr is creating the task:
inTraining <- caret::createDataPartition(datII$yield, p = 0.80, list = FALSE)
training <- datII[inTraining, ]
testing <- datII[-inTraining, ]

# For tuneRanger, a mlr task has to be created:
soy.task <- mlr::makeRegrTask(data = as.data.frame(training), target = "yield")

### Ref: Probst et al and the tuneRanger documentation
# Rough estimation of the tuning time
# estimateTimeTuneRanger(soy.task)

# Tuning process:
rf3 <- tuneRanger(soy.task, num.trees = 1500)

# Mean of best 5 % of the results:
rf3
# Model with the new tuned hyperparameters:
rf3$model

# Recommended parameters:
rf3$recommended.pars

# the OOB RMSE:
sqrt(rf3$model$learner.model$prediction.error)
```


### Predictions on the test data
```{r RF-Test-Fit, eval=FALSE, echo=FALSE}
# Use tuned parameters from tuneRanger:
fit <- ranger::ranger(yield ~ ., data = training, 
                      num.trees = 1500, 
                      mtry = 5, 
                      importance = "impurity", 
                      min.node.size = 2, 
                      replace = FALSE,
                      sample.fraction =  0.88,
                      respect.unordered.factors = 'order',
                      seed = 14092)


# The predicted values vs actual values on the test data:
# The graph below shows the predictions on the test data for the RF model tuned on the training data. There is a tendency to under-predict high yields, and to over-predict the low yields.

data.frame(actual = testing$yield, rngr = predict(fit, data = testing)$predictions, MG = testing$MG) %>%
  ggplot(., aes(x = actual, y = rngr, colour = MG)) + 
  geom_point(alpha = 0.5) + 
  scale_color_brewer(type = "qual", palette = "Set1", direction = 1) +
  theme_bw() +
  coord_fixed(xlim = c(0.5, 6), ylim = c(0.5, 6)) +
  geom_smooth(aes(x = actual, y = rngr), method = lm, inherit.aes = FALSE) +
  geom_segment(aes(x = 0.5, xend = 6, y = 0.5, yend = 6), size = 1, colour = "black") +
  ylab("Predicted yield (t/ha)") + 
  xlab("Actual yield (t/ha)") +
  theme(axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 12, hjust = 0.5),
        axis.title.x = element_text(size = 14), axis.title.y = element_text(size = 14)) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "vertical") +
  # override the transparency of the points for the legend:
  guides(colour = guide_legend(nrow = 1, title = "Maturity group", override.aes = list(alpha = 1)))
```


## Finalized model
The finalized (tuned) random forest model is refit to the full data using the `ranger` package.

We also use 3,000 trees for stability in the permutation-based variable importance measure (see Probst et al. WIRES article). Permutation-based variable importance is preferred over Gini variable importance measures because the latter is biased. 

```{r RF-Fulldata, eval=TRUE, echo=FALSE}
# A bit of clean up:
rm(list = ls()[!(ls() %in% c("dat", "datII", "soy2", "states"))]) 

# Fit a random forest (impurity-based variable importance):
rfo <- ranger::ranger(yield ~ ., data = datII, 
                      num.trees = 3000, 
                      mtry = 5, 
                      importance = "impurity", 
                      min.node.size = 2, 
                      replace = FALSE,
                      sample.fraction =  0.88,
                      respect.unordered.factors = 'order',
                      seed = 14092)
```



------------------------------------------------------------------------------------------------


# Model interpretations {.tabset .tabset-fade .tabset-pills}
## Residuals  {.tabset .tabset-fade .tabset-pills}

Residuals = actual - predicted yield  

Scatterplot: The residuals show that yields are being over-predicted (negative residuals) at low yields, and under-predicted (positive residuals) at high yields.

### Version 1
<!-- Supplementary Figure S2 -->
```{r ResidualsScatterplotI, eval=TRUE, echo=FALSE, results='hide'}
predicted <- predict(rfo, data = datII)$predictions
residuals <- datII$yield - predicted

# RMSE:
sqrt(sum(residuals^2)/nrow(datII))

# Predicted yield (t/ha) summary statistics:
round(mean(predicted), digits = 2)
round(min(predicted), digits = 2)
round(max(predicted), digits = 2)
round(sd(predicted)  , digits = 2)


# Plotting...
# options(repr.plot.width = 8, repr.plot.height = 4)
# Plot residuals vs predicted yield:
data.frame(predicted = predicted, residuals = residuals, MG = datII$MG) %>%
ggplot(., aes(x = predicted, y = residuals, colour = MG)) + 
  geom_point(alpha = 0.5) + 
  geom_smooth(aes(x = predicted, y = residuals), method = lm, inherit.aes = FALSE) +
  scale_color_brewer(type = "qual", palette = "Set1", direction = 1) +
  theme_bw() +
  ylab("Residual (t/ha)") + 
  xlab("Predicted yield (t/ha)") + 
  theme(axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 12, hjust = 0.5),
        axis.title.x = element_text(size = 14, face = "bold"), 
        axis.title.y = element_text(size = 14, face = "bold")) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "vertical") +
  # override the transparency of the points for the legend:
  guides(colour = guide_legend(nrow = 1, title = "Maturity group", override.aes = list(alpha = 1)))
```


### Version 2
```{r ResidualsScatterplotII, eval=TRUE, echo=FALSE}
# Another option is to have each MG in its own panel:
data.frame(predicted = predicted, residuals = residuals, MG = datII$MG) %>%
ggplot(., aes(x = predicted, y = residuals, colour = MG)) + 
  geom_point(alpha = 0.5) + 
  facet_wrap(~ MG) +
  geom_smooth(aes(x = predicted, y = residuals), method = lm, inherit.aes = FALSE) +
  scale_color_brewer(type = "qual", palette = "Set1", direction = 1) +
  theme_bw() +
  ylab("Residual (t/ha)") + 
  xlab("Predicted yield (t/ha)") + 
  theme(axis.text.y = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0.5),
        axis.title.x = element_text(size = 14), 
        axis.title.y = element_text(size = 14),
        # Bold the facet text labels:
        strip.text = element_text(face = "bold")) +
  # move the legend into where there was empty facet space
  theme(legend.position = c(0.9, -0.01), legend.justification = c(1, 0)) +
  # override the transparency of the points for the legend:
  guides(colour = guide_legend(title = "Maturity group", override.aes = list(alpha = 1)))
```



--------------------------------------------------------------------------------------------------


## Global interpretation of machine learning models {.tabset .tabset-fade .tabset-pills}
Global interpretation is through: 

* variable (feature) importance measures  
* partial dependence plots 
* ICE curves

### Feature importance
```{r iml-setup, eval=TRUE, echo=FALSE}
# Load iml feature importance and interaction results:
load("~/EskerSoybean/Manuscripts/TommyPaperAnalysisII/imlResults.RData")
```


<!-- Figure 1 -->
```{r iml-FeatureImportance-Plot, eval=TRUE, echo=FALSE}
# Note: to reproduce the plot that is given by plot(iml.imp), I looked into the iml code on GitHub: https://github.com/christophM/iml/tree/master/R

iml.imp.results %>%
  # Renaming variables for more descriptive labels:
  dplyr::mutate(feature = replace(feature, feature == "doy", "Sowing date")) %>%
  dplyr::mutate(feature = replace(feature, feature == "latitude", "Latitude")) %>%
  dplyr::mutate(feature = replace(feature, feature == "pH.0.30.cm", "Topsoil pH")) %>%
  dplyr::mutate(feature = replace(feature, feature == "OM.0.30.cm", "Topsoil organic matter")) %>%
  dplyr::mutate(feature = replace(feature, feature == "seed.rate", "Seeding rate")) %>%
  dplyr::mutate(feature = replace(feature, feature == "GDD", "Growing degree days")) %>%
  dplyr::mutate(feature = replace(feature, feature == "foliar.fungicide", "Used a foliar fungicide")) %>%
  dplyr::mutate(feature = replace(feature, feature == "AI", "Aridity index")) %>%
  dplyr::mutate(feature = replace(feature, feature == "MG.f", "Soybean maturity group")) %>%
  dplyr::mutate(feature = replace(feature, feature == "foliar.insecticide", "Used a foliar insecticide")) %>%
  dplyr::mutate(feature = replace(feature, feature == "texture.0.30", "Topsoil texture")) %>%
  dplyr::mutate(feature = replace(feature, feature == "TWI", "Topographic wetness index")) %>%
  dplyr::mutate(feature = replace(feature, feature == "herbicide", "Herbicide program")) %>%
  dplyr::mutate(feature = replace(feature, feature == "row.space", "Row spacing")) %>%
  dplyr::mutate(feature = replace(feature, feature == "seed.trt1", "Used a seed treatment")) %>%
  dplyr::mutate(feature = replace(feature, feature == "starter.fert", "Used a starter fertilizer")) %>%
  dplyr::mutate(feature = replace(feature, feature == "lime", " Applied lime")) %>%
  dplyr::mutate(feature = replace(feature, feature == "manure", "Applied manure")) %>%
  dplyr::mutate(feature = replace(feature, feature == "iron.def", "Iron deficiency symptoms")) %>%
  dplyr::mutate(feature = replace(feature, feature == "PAWR", "Plant available water holding\ncapacity in the rooting zone")) %>%
  
  # want higher importance to appear at the top of the plot:
  dplyr::arrange(importance) %>%
  dplyr::mutate(feature = factor(feature, levels = .$feature)) %>%
  ggplot(., aes(y = feature, x = importance)) +  
  geom_segment(aes(y = feature, yend = feature, x = importance.05, xend = importance.95), size = 1.5, 
               color = "darkslategrey") +
  geom_point(size = 3) +
  theme_bw() +
  scale_x_continuous(name = "Feature importance (ratio)", limits = c(1, NA)) + 
  scale_y_discrete(name = NULL) +
  theme(axis.title.x = element_text(face = "bold", size = 11)) + 
  theme(axis.title.y = element_text(face = "bold", size = 11))
```

### Two-way partial dependence plots {.tabset .tabset-fade .tabset-pills}
#### doy and latitude
doy and latitude were the two most important features from the global model perspective

<!-- Supplementary Figure S3 -->
```{r MPDP-latitude-doy, eval=TRUE, echo=FALSE}
load("~/EskerSoybean/Manuscripts/TommyPaperAnalysisII/MPDPII.RData")

mpdp.lat.doy %>%
  # Convert yield from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
  dplyr::mutate(yhat = yhat*0.06725) %>%
  wireframe(yhat ~ latitude*doy, data = .,
            xlab = "Latitude", ylab = "Sowing date", zlab = "Yield",
            main = NULL,
            drape = TRUE,
            colorkey = TRUE,
            screen = list(z = -60, x = -60)
            )
```


#### doy, latitude  and fungicide
Features with the strongest two-way interactions were latitude, doy and foliar.fungicide. Therefore, we estimated the 2-way pdp for: (i) doy and fungicide, (ii) latitude and fungicide. Then plot the difference in yield between the pdp fungicide curves.

<!-- Figure 2 -->
```{r iml-PDP-doy-latitude-fungicide, eval=TRUE, echo=FALSE}
# doy
p1 <-
inter.pdp.doy.fungicide.res %>%
  dplyr::select(doy, foliar.fungicide, .y.hat) %>%
  dplyr::rename(yld = .y.hat) %>%
  dplyr::mutate(yld = yld*0.06725) %>%
  tidyr::spread(., foliar.fungicide, yld) %>%
  dplyr::mutate(ylddiff = yes - no) %>%
  ggplot(., aes(x = doy, y = ylddiff)) +
  geom_line(size = 1) +
  geom_smooth(method = loess, se = FALSE, span = 0.1) +
  geom_rug(data = dat, aes(x = doy, y = 0), inherit.aes = FALSE, position = "jitter", sides = "b", 
           size = 0.1, alpha = 0.3) +
  ylim(-0.1, 0.4) +
  theme_bw() +
  ylab("Yield difference (t/ha) sprayed - unsprayed") + 
  xlab("Sowing date (day of year)") + 
  theme(axis.text.y = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0.5),
        axis.title.x = element_text(size = 13, face = "bold"), 
        axis.title.y = element_text(size = 13, face = "bold"))

# latitude
p2 <-
inter.pdp.fungicide.latitude.res %>%
  dplyr::select(latitude, foliar.fungicide, .y.hat) %>%
  dplyr::rename(yld = .y.hat) %>%
  # convert to t/ha
  dplyr::mutate(yld = yld*0.06725) %>%
  # to be able to calculate the difference in yield between the sprayed and unsprayed curves
  tidyr::spread(., foliar.fungicide, yld) %>%
  dplyr::mutate(ylddiff = yes - no) %>%
  ggplot(., aes(x = latitude, y = ylddiff)) +
  geom_line(size = 1) +
  geom_smooth(method = loess, se = FALSE, span = 0.1) +
  # to add a rug of the data positions:
  geom_rug(data = dat, aes(x = latitude, y = 0), inherit.aes = FALSE, position = "jitter", sides = "b", 
           size = 0.1, alpha = 0.3) +
  ylim(-0.1, 0.4) +
  # want some more tick mark labels than the default:
  scale_x_continuous(breaks = seq(37, 51, 2)) +
  theme_bw() +
  ylab("Yield difference (t/ha) sprayed - unsprayed") + 
  xlab("Latitude") + 
  theme(axis.text.y = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0.5),
        axis.title.x = element_text(size = 13, face = "bold"), 
        axis.title.y = element_text(size = 13, face = "bold"))


grid.arrange(p1, p2, ncol = 2)
```




--------------------------------------------------------------------------------------------------


# Top 12 TEDs {.tabset .tabset-fade .tabset-pills}
## By MG
<!-- Supplementary Figure S4 -->
```{r lime-TED-map-top12-by-MG, eval=TRUE, echo=FALSE}
# Filter to the top 12 TEDs:
top.12.TEDs <- dat %>% dplyr::count(TED) %>% dplyr::arrange(-n) %>% dplyr::slice(1:12) %>% dplyr::pull(TED) 

# Map the field locations for the top 12 TEDs
ggplot() +
  geom_sf(data = soy2) +
  theme_bw() +
  geom_point(data = dat %>% 
               dplyr::filter(TED %in% top.12.TEDs), 
             aes(x = longitude, y = latitude, colour = MG), alpha = 0.5, size = 1.5) +
  scale_color_brewer(type = "qual", palette = "Set1", direction = 1) +
  facet_wrap(~ TED) +
  xlab("Longitude") +
  ylab("Latitude") +
  theme(axis.title.x = element_text(face = "bold", size = 13),
        axis.text.x  = element_text(size = 9, angle = 90),
        axis.title.y = element_text(size = 13, angle = 90, face = "bold"),
        axis.text.y  = element_text(size = 9),
        # Bold the facet text labels:
        strip.text = element_text(face = "bold")) +
  guides(colour = guide_legend(nrow = 1, title = "Maturity group", override.aes = list(alpha = 1))) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "vertical")
```

## By PAWR 
```{r lime-TED-map-top12-by-PAWR, eval=TRUE, echo=FALSE}
# Map the field locations for the top 12 TEDs
ggplot() +
  geom_sf(data = soy2) +
  theme_bw() +
  geom_point(data = dat %>% 
               dplyr::filter(TED %in% top.12.TEDs), 
             aes(x = longitude, y = latitude, colour = PAWR), alpha = 0.5, size = 1.0) +
  scale_color_brewer(type = "qual", palette = "Set1", direction = 1) +
  facet_wrap(~ TED) +
  xlab("Longitude") +
  ylab("Latitude") +
  theme(axis.title.x = element_text(face = "bold", size = 12),
        axis.text.x  = element_text(size = 8, angle = 90),
        axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
        axis.text.y  = element_text(size = 8),
        # Bold the facet text labels:
        strip.text = element_text(face = "bold")) +
  guides(colour = guide_legend(nrow = 1, title = "PAWR", override.aes = list(alpha = 1))) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "vertical")
```

## By GDD
```{r lime-TED-map-top12-by-GDD, eval=TRUE, echo=FALSE}
# Map the field locations for the top 12 TEDs
ggplot() +
  geom_sf(data = soy2) +
  theme_bw() +
  geom_point(data = dat %>% 
               dplyr::filter(TED %in% top.12.TEDs), 
             aes(x = longitude, y = latitude, colour = GDD), alpha = 0.5, size = 1.0) +
  scale_color_brewer(type = "qual", palette = "Set1", direction = 1) +
  facet_wrap(~ TED) +
  xlab("Longitude") +
  ylab("Latitude") +
  theme(axis.title.x = element_text(face = "bold", size = 12),
        axis.text.x  = element_text(size = 8, angle = 90),
        axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
        axis.text.y  = element_text(size = 8),
        # Bold the facet text labels:
        strip.text = element_text(face = "bold")) +
  guides(colour = guide_legend(nrow = 1, title = "GDD", override.aes = list(alpha = 1))) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "vertical")
```

## By AI
```{r lime-TED-map-top12-by-AI, eval=TRUE, echo=FALSE}
# Map the field locations for the top 12 TEDs
ggplot() +
  geom_sf(data = soy2) +
  theme_bw() +
  geom_point(data = dat %>% 
               dplyr::filter(TED %in% top.12.TEDs), 
             aes(x = longitude, y = latitude, colour = AI), alpha = 0.5, size = 1.0) +
  scale_color_brewer(type = "qual", palette = "Set1", direction = 1) +
  facet_wrap(~ TED) +
  xlab("Longitude") +
  ylab("Latitude") +
  theme(axis.title.x = element_text(face = "bold", size = 12),
        axis.text.x  = element_text(size = 8, angle = 90),
        axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
        axis.text.y  = element_text(size = 8),
        # Bold the facet text labels:
        strip.text = element_text(face = "bold")) +
  guides(colour = guide_legend(nrow = 1, title = "AI", override.aes = list(alpha = 1))) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "vertical")
```




# Shapley
```{r Shapley-Load-FittedObjects, eval=TRUE, echo=FALSE}
load("~/EskerSoybean/Manuscripts/TommyPaperAnalysisII/ShapFits.RData")
```

## HYF vs HYNF {.tabset .tabset-fade .tabset-pills}
### Figure
<!-- Figure 3 -->
```{r shap-Comparisons-Top12-HYF-HYNF, eval=TRUE, echo=FALSE}
# Now you want to generalize for any TED, iterating over the sample_id in the TED, for any one of HYF, HYNF, LYF, LYNF:
fx <- function(.dat, .TED) {
  # for any one of HYF.shap, HYNF.shap, LYF.shap, LYNF.shap, iterate over sample_id in a TED and get the yield difference and phi values along with other information for plotting
  # Args:
  #  .dat = one of HYF.shap, HYNF.shap, LYF.shap, LYNF.shap
  #  .TED = a TED in one of the .shap files
  # Returns:
  #  a data frame of extracted phi and other components for each field
  #
  # Number of sample_id (fields) in a given TED:
  sl <- purrr::pluck(.dat, .TED, "sample_id") %>% length()
  
  # Iterate over all the sample_id in the TED:
  purrr::map_df(1:sl, function(.i) {
    purrr::pluck(.dat, .TED) %>% 
      dplyr::slice(.i) %>% 
      dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
      dplyr::mutate(mn = purrr::map_dbl(shap, purrr::pluck, "mean")) %>%
      dplyr::mutate(ylddiff = actual - mn) %>%
      dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "foliar.fungicide") %>%
          dplyr::pull(phi)})) %>%
      dplyr::mutate(fung = purrr::map_chr(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "foliar.fungicide") %>%
          dplyr::select(feature.value) %>%
          stringr::str_remove(".*=")})) %>%
      dplyr::mutate(TED = .TED) %>%
      dplyr::select(sample_id, TED, ylddiff, phi, fung)
  }
  )
}  # end fx


# Example of use:
# fx(.dat = HYNF.shap, .TED = "303603")

# Now apply fx over all the TEDs, for HYF and HYNF and bind into a data.frame:
HY <-
  dplyr::bind_rows(
  purrr::map_df(HYF.shap %>% names(), fx, .dat = HYF.shap),
  purrr::map_df(HYNF.shap %>% names(), fx, .dat = HYNF.shap)) %>%
  dplyr::mutate(TED = factor(TED, levels = c("303603", "303703", "403603", "403703", "504803", "602303", "603503", "603603", "603703", "604503", "604603", "604803"))) %>%
  dplyr::mutate(fung = factor(fung, levels = c("no", "yes"), labels = c("Unsprayed", "Sprayed")))

# and now plot...
HY %>%
  # Convert yield from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
  dplyr::mutate(ylddiff = ylddiff*0.06725) %>%
  dplyr::mutate(phi = phi*0.06725) %>%
  ggplot(., aes(x = ylddiff, y = phi, colour = fung)) +
  geom_point(alpha = 0.5, size = 2.0) +
  # Based on RColorbrewer qualitative set 1:
  scale_color_manual(values = c("#377eb8", "#ff7f00")) + 
  theme_bw() +
  # geom_hline(yintercept = 0, linetype = 2) +
  geom_hline(aes(yintercept = 0), color = "gray70", size = 0.6) +
  geom_vline(aes(xintercept = 0), color = "gray70", size = 0.6) +
  facet_wrap(~ TED) +
  # ylab("phi value (t/ha)") +
  ylab(expression(bolditalic("phi")~bold(" value (t/ha)"))) +
  xlab("Single field predicted yield - mean predicted yield (t/ha)") +
  theme(axis.title.x = element_text(face = "bold", size = 13),
        axis.text.x  = element_text(size = 10, angle = 0),
        # axis.title.y = element_text(size = 13, angle = 90, face = "bold"),
        axis.title.y = element_text(size = 13, angle = 90),
        axis.text.y  = element_text(size = 10),
        # Bold the facet text labels:
        strip.text = element_text(face = "bold", size = 10)) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "horizontal") +
  # override the transparency of the points for the legend:
  guides(colour = guide_legend(nrow = 1, title = "Foliar fungicide", override.aes = list(alpha = 1)))
```

### Summary as a Table
```{r shap-Comparisons-Top12-HYF-HYNF-Table, eval=TRUE, echo=FALSE}
# GOAL: Summary of the predicted yields, phi values, for each TED and cohort (sprayed, unsprayed) within TED

# Define a helper function to extract the relevant parts from the .shap objects
fx1 <- function(.dat, .TED) {
  # for any one of HYF.shap, HYNF.shap, LYF.shap, LYNF.shap, iterate over sample_id in a TED and get the predicted yield and phi values per field
  # Args:
  #  .dat = one of HYF.shap, HYNF.shap, LYF.shap, LYNF.shap
  #  .TED = a TED in one of the .shap files
  # Returns:
  #  a data frame of extracted predicted yield, phi and other components for each field
  #
  # Number of sample_id (fields) in a given TED:
  sl <- purrr::pluck(.dat, .TED, "sample_id") %>% length()
  
  # Iterate over all the sample_id in the TED:
  purrr::map_df(1:sl, function(.i) {
    purrr::pluck(.dat, .TED) %>% 
      dplyr::slice(.i) %>% 
      # Get the predicted yield:
      dplyr::mutate(pred = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
      # Get the phi values associated with foliar fungicide:
      dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "foliar.fungicide") %>%
          dplyr::pull(phi)})) %>%
      dplyr::mutate(fung = purrr::map_chr(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "foliar.fungicide") %>%
          dplyr::select(feature.value) %>%
          stringr::str_remove(".*=")})) %>%
      dplyr::mutate(TED = .TED) %>%
      dplyr::select(sample_id, TED, pred, phi, fung)
  }
  )
}  # end fx1

# Now apply fx1 over all the TEDs, for HYF and HYNF and bind into a data.frame:
HYdat <-
  dplyr::bind_rows(
  purrr::map_df(HYF.shap %>% names(), fx1, .dat = HYF.shap),
  purrr::map_df(HYNF.shap %>% names(), fx1, .dat = HYNF.shap)) %>%
  dplyr::mutate(TED = factor(TED, levels = c("303603", "303703", "403603", "403703", "504803", "602303", "603503", "603603", "603703", "604503", "604603", "604803"))) %>%
  dplyr::mutate(fung = factor(fung, levels = c("no", "yes"), labels = c("Unsprayed", "Sprayed"))) %>%
  # Convert yield from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
  dplyr::mutate(pred = pred*0.06725) %>%
  dplyr::mutate(phi = phi*0.06725)

# Output the Table:
HYdat %>%
  dplyr::group_by(TED, fung) %>%
  dplyr::summarise_at(c("pred", "phi"), list(~min(.), ~max(.), ~mean(.))) %>%
  dplyr::select(TED, fung, starts_with("pred"), starts_with("phi")) %>%
  knitr::kable(., row.names = FALSE, digits = 3, align = "llcccccc", col.names = c("TED", "Fungicide", "Min", "Max", "Mean", "Min", "Max", "Mean")) %>%
  kableExtra::kable_styling("striped") %>%
  kableExtra::add_header_above(c(" " = 2, "Predicted Yield (t/ha)" = 3, "Phi (t/ha)" = 3))

# The overall means among the sprayed and unsprayed fields across all 12 TEDs:
HYdat %>%
  dplyr::group_by(fung) %>%
  dplyr::summarise(ave.pred = mean(pred), ave.phi = mean(phi))
```


### Summary of the $\phi$ values
<!-- Supplementary Figure S5 -->
```{r shap-Comparisons-Top12-HYF-HYNF-Figure, eval=TRUE, echo=FALSE, fig.keep='last'}
# str(HYdat)

# Field order (sprayed, by phi):
ted.order <- 
  HYdat %>%
  dplyr::filter(fung == "Sprayed") %>%
  dplyr::group_by(TED) %>%
  dplyr::summarise(ave = mean(phi)) %>%
  # want higher mean yield to appear at the bottom of the plot:
  dplyr::arrange(desc(ave)) %>%
  dplyr::pull(TED) %>%
  as.character()

# GOAL: plot the mean predicted yield per TED, with TEDs sorted by ted.order, jitter for the yields of the individual fields within TEDs:
HYdat %>%
  dplyr::filter(fung == "Sprayed") %>%
  dplyr::mutate(TED = factor(TED, levels = ted.order)) %>%
  ggplot(., aes(x = TED, y = pred, colour = TED)) +
  coord_flip() +
  geom_jitter(position = position_jitter(seed = 2019, width = 0.1), size = 2, alpha = 0.25) +
  stat_summary(fun.y = "mean", geom = "point", size = 5) +
  scale_color_viridis_d(option = "D") +
  labs(x = "TED", y = "Predicted yield (t/ha)") +
  theme_bw() +
  ggtitle("A") +
  theme(
    legend.position = "none",
    axis.title.x = element_text(face = "bold", size = 12),
    axis.text.x  = element_text(size = 9, angle = 0),
    axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
    axis.text.y  = element_text(size = 9),
    panel.grid = element_blank(),
    plot.title = element_text(face = "bold")
    )


# Generalize to a function:
fxn <- function(.df, .fung, .var, .ylab, my.title, LL, UL) {
  #
  # Args:
  #  .df = data frame with the TEDs, foliar fungicide, predicted yield, phi for fungicide
  #  .fung = character string for fungicide ("Sprayed", "Unsprayed")
  #  .var = unquoted string for predicted yield (pred) or phi (phi)
  #  .ylab = character string for the y-axis label
  #  my.title = character string for the plot title
  #  LL = 
  #  UL =
  #
  # Returns:
  #  plot of the predicted yield or phi for fungicide for individual fields in each TED, plus the mean
  #
  var <- enquo(.var)
  
  # the overall mean across all TEDs:
  smry <- .df %>%
    dplyr::filter(fung == .fung) %>%
    dplyr::select(!!var) %>%
    dplyr::summarise(mn = mean(!!var)) %>%
    dplyr::pull(mn)
    
  
  .df %>%
  dplyr::filter(fung == .fung) %>%
  dplyr::mutate(TED = factor(TED, levels = ted.order)) %>%
  ggplot(., aes(x = TED, y = !!var, colour = TED)) +
  coord_flip() +
  # line representing the overall mean:
  geom_hline(aes(yintercept = smry), color = "gray70", size = 0.6) +
  geom_jitter(position = position_jitter(seed = 2019, width = 0.1), size = 2, alpha = 0.25) +
  stat_summary(fun.y = "mean", geom = "point", size = 5) +
  scale_color_viridis_d(option = "D") +
  scale_y_continuous(limits = c(LL, UL), expand = c(0.005, 0.005)) +
  labs(x = NULL, y = .ylab) +
  theme_bw() +
  ggtitle(my.title) +
  theme(
    legend.position = "none",
    axis.title.x = element_text(face = "bold", size = 12),
    axis.text.x  = element_text(size = 9, angle = 0),
    axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
    axis.text.y  = element_text(size = 9),
    panel.grid = element_blank(),
    plot.title = element_text(face = "bold")
    )
} # end function


# h1 <- fxn(.df = HYdat, .fung = "Sprayed", .var = pred, .ylab = "Predicted yield (t/ha)", my.title = "Sprayed", LL = 1.5, UL = 7.0)  
# h2 <- fxn(.df = HYdat, .fung = "Unsprayed", .var = pred, .ylab = "Predicted yield (t/ha)", my.title = "Unsprayed", LL = 1.5, UL = 7.0)  
# h3 <- fxn(.df = HYdat, .fung = "Sprayed", .var = phi, .ylab = "Phi (t/ha)", my.title = "Sprayed", LL = -0.15, UL = 0.4)
# h4 <- fxn(.df = HYdat, .fung = "Unsprayed", .var = phi, .ylab = "Phi (t/ha)", my.title = "Unsprayed", LL = -0.15, UL = 0.4)  
# 
# grid.arrange(h1, h3, h2, h4, ncol = 2)

h1 <- fxn(.df = HYdat, .fung = "Sprayed", .var = pred, .ylab = "Predicted yield (t/ha)", my.title = "Sprayed", LL = 1.5, UL = 7.0)  
h2 <- fxn(.df = HYdat, .fung = "Unsprayed", .var = pred, .ylab = "Predicted yield (t/ha)", my.title = "Unsprayed", LL = 1.5, UL = 7.0)  
h3 <- fxn(.df = HYdat, .fung = "Sprayed", .var = phi, .ylab = expression(bolditalic("phi")~bold(" (t/ha)")), my.title = "Sprayed", LL = -0.15, UL = 0.4)
h4 <- fxn(.df = HYdat, .fung = "Unsprayed", .var = phi, .ylab = expression(bolditalic("phi")~bold(" (t/ha)")), my.title = "Unsprayed", LL = -0.15, UL = 0.4)  

grid.arrange(h1, h3, h2, h4, ncol = 2)
```




## AllHYF.shap, AllHYNF.shap, AllLYF.shap, AllLYNF.shap {.tabset .tabset-fade .tabset-pills}
### Main Figure

```{r shap-Comparisons-All-TableInsert, eval=TRUE, echo=FALSE}
## Code for an Insert table

# No. fields, min, max and mean predicted yields by cohort (sprayed x yield category)

# Define a helper function:
fxb <- function(.dat, .yldenv) {
  
  # Extract the predicted yields from one of the Allxx.shap objects.
  # Args:
  #  .dat = one of AllHYF.shap, AllHYNF.shap, AllLYF.shap, AllLYNF.shap
  #  .yldenv = character string for best- or worst-yielding fields ("Low", "High")
  # Returns:
  #  a data frame of the extracted values
  #
  # Iterate over all the sample_id (there are 100 fields in each of the `All` groups:
  purrr::map_df(1:100, function(.i) {
      .dat %>%
      dplyr::slice(.i) %>% 
      dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
      dplyr::mutate(fung = purrr::map_chr(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "foliar.fungicide") %>%
          dplyr::select(feature.value) %>%
          stringr::str_remove(".*=")})) %>%
      dplyr::mutate(yldenv = .yldenv) %>%
      dplyr::select(sample_id, actual, fung, yldenv)
  }
  )
}  # end fxb

# Prep the data:
d.tab <- 
  dplyr::bind_rows(fxb(.dat = AllHYF.shap, .yldenv = "Highest yielding"),
                   fxb(.dat = AllHYNF.shap, .yldenv = "Highest yielding"),
                   fxb(.dat = AllLYF.shap, .yldenv = "Lowest yielding"),
                   fxb(.dat = AllLYNF.shap, .yldenv = "Lowest yielding")) %>%
  dplyr::mutate(yldenv = factor(yldenv, levels = c("Lowest yielding", "Highest yielding"))) %>%
  dplyr::mutate(fung = factor(fung, levels = c("no", "yes"), labels = c("Unsprayed", "Sprayed"))) %>%
  # Convert yield from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
  dplyr::mutate(actual = actual*0.06725) %>%
  dplyr::group_by(fung, yldenv) %>%
  dplyr::summarise(`No. fields` = n(), `Min Yield` = min(actual), `Max Yield` = max(actual), `Mean Yield` = mean(actual)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(`Min Yield` = sprintf("%.1f", `Min Yield`),
                `Max Yield` = sprintf("%.1f", `Max Yield`),
                `Mean Yield` = sprintf("%.1f", `Mean Yield`)) %>%
  dplyr::rename(Fungicide = fung, Cohort = yldenv)
```


<!-- Figure 4 -->
```{r shap-Comparisons-All-Figure, eval=TRUE, echo=FALSE}
# Define a helper function:
fxa <- function(.dat, .yldenv) {
  # Extract the phi values from one of the Allxx.shap objects.
  # Args:
  #  .dat = one of AllHYF.shap, AllHYNF.shap, AllLYF.shap, AllLYNF.shap
  #  .yldenv = character string for best- or worst-yielding fields ("Low", "High")
  # Returns:
  #  a data frame of the extracted values
  #
  # Iterate over all the sample_id (there are 100 fields in each of the `All` groups:
  purrr::map_df(1:100, function(.i) {
      .dat %>%
      dplyr::slice(.i) %>% 
      dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
      dplyr::mutate(mn = purrr::map_dbl(shap, purrr::pluck, "mean")) %>%
      dplyr::mutate(ylddiff = actual - mn) %>%
      dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "foliar.fungicide") %>%
          dplyr::pull(phi)})) %>%
      dplyr::mutate(fung = purrr::map_chr(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "foliar.fungicide") %>%
          dplyr::select(feature.value) %>%
          stringr::str_remove(".*=")})) %>%
      dplyr::mutate(yldenv = .yldenv) %>%
      dplyr::select(sample_id, ylddiff, phi, fung, yldenv)
  }
  )
}  # end fxa

# Prep the data:
alldf <- 
dplyr::bind_rows(fxa(.dat = AllHYF.shap, .yldenv = "Highest yielding"),
                 fxa(.dat = AllHYNF.shap, .yldenv = "Highest yielding"),
                 fxa(.dat = AllLYF.shap, .yldenv = "Lowest yielding"),
                 fxa(.dat = AllLYNF.shap, .yldenv = "Lowest yielding")) %>%
  dplyr::mutate(yldenv = factor(yldenv, levels = c("Lowest yielding", "Highest yielding"))) %>%
  dplyr::mutate(fung = factor(fung, levels = c("no", "yes"), labels = c("Unsprayed", "Sprayed"))) %>%
  # Convert yield from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
  dplyr::mutate(ylddiff = ylddiff*0.06725) %>%
  dplyr::mutate(phi = phi*0.06725)
  

# Now plot:
alldf %>%
  ggplot(., aes(x = ylddiff, y = phi, colour = fung, shape = yldenv)) +
  geom_point(alpha = 0.5, size = 2.0) +
  # Based on RColorbrewer qualitative set 1:
  scale_color_manual(values = c("#377eb8", "#ff7f00")) + 
  # Don't use the same point symbols for foliar fungicide (circles) and yldenv:
  scale_shape_manual(values = c(15 ,17)) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = 2) +
  # ylab("Phi value (t/ha)") +
  ylab(expression(bolditalic("phi")~bold(" value (t/ha)"))) +
  xlab("Single field predicted yield - mean predicted yield (t/ha)") +
  theme(axis.title.x = element_text(face = "bold", size = 13),
        axis.text.x  = element_text(size = 11, angle = 0),
        # axis.title.y = element_text(size = 13, angle = 90, face = "bold"),
        axis.title.y = element_text(size = 13, angle = 90),
        axis.text.y  = element_text(size = 11)) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "horizontal") +
  # override the transparency of the points for the legend:
  guides(shape = guide_legend(nrow = 1, title = "Field", override.aes = list(alpha = 1)), 
         colour = guide_legend(nrow = 1, title = "Foliar fungicide", override.aes = list(alpha = 1))) +
  # Use the rowhead argument to set the labels to non-italic bold:
  # rows = NULL prevents row numbers from being printed with the Table:
  annotation_custom(gridExtra::tableGrob(d.tab, rows = NULL, theme = ttheme_default(base_size = 8, rowhead = list(fg_params = list(col = "black", fontface = 2L)))), xmin = -2.1, xmax = 0, ymin = 0.2, ymax = 0.45)
```


### Histogram of the $\phi$ values
```{r shap-Comparisons-All-Histo, eval=TRUE, echo=FALSE}
alldf %>%
  ggplot(., aes(x = phi)) +
  geom_histogram(binwidth = .01, fill = "grey90", colour = "black") +
  facet_grid(yldenv ~ fung) +
  theme_bw() +
  geom_vline(xintercept = 0, colour = "grey50", linetype = "dashed") +
  xlab("Phi value (t/ha)") +
  ylab("No. fields") +
  theme(axis.title.x = element_text(face = "bold", size = 12),
        axis.text.x  = element_text(size = 6, angle = 0),
        axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
        axis.text.y  = element_text(size = 6))
```


### Tabular summary of the $\phi$ values
```{r shap-Comparisons-All-Summary-Table, eval=TRUE, echo=FALSE}
alldf %>%
  dplyr::group_by(yldenv, fung) %>%
  dplyr::summarise(mean = mean(phi), min = min(phi), max = max(phi))
```

### Plot summary of the $\phi$ values
<!-- Supplementary Figure S6 -->
```{r shap-Comparisons-All-Summary-Fig, eval=TRUE, echo=FALSE}
# str(alldf)

alldf %>%
  # Create labels:
  dplyr::mutate(lbs = "N.A.") %>%
  dplyr::mutate(lbs = replace(lbs, fung == "Sprayed" & yldenv == "Highest yielding", "Sprayed (HY)")) %>%
  dplyr::mutate(lbs = replace(lbs, fung == "Sprayed" & yldenv == "Lowest yielding", "Sprayed (LY)")) %>%
  dplyr::mutate(lbs = replace(lbs, fung == "Unsprayed" & yldenv == "Highest yielding", "Unsprayed (HY)")) %>%
  dplyr::mutate(lbs = replace(lbs, fung == "Unsprayed" & yldenv == "Lowest yielding", "Unsprayed (LY)")) %>%
  dplyr::mutate(lbs = factor(lbs, levels = c("Unsprayed (LY)", "Unsprayed (HY)", "Sprayed (LY)", "Sprayed (HY)"))) %>%
  ggplot(., aes(x = lbs, y = phi, colour = fung, shape = yldenv)) +
  coord_flip() +
  geom_jitter(position = position_jitter(seed = 2019, width = 0.1), size = 2, alpha = 0.25) +
  stat_summary(fun.y = "mean", geom = "point", size = 5) +
  # Based on RColorbrewer qualitative set 1:
  scale_color_manual(values = c("#377eb8", "#ff7f00")) + 
  # labs(x = NULL, y = "Phi value (t/ha)") +
  labs(x = NULL, y = expression(bolditalic("phi")~bold(" value (t/ha)"))) +
  theme_bw() +
  theme(
    legend.position = "none",
    axis.title.x = element_text(face = "bold", size = 13),
    axis.text.x  = element_text(size = 10, angle = 0),
    axis.title.y = element_text(size = 13, angle = 90, face = "bold"),
    axis.text.y  = element_text(size = 10),
    panel.grid = element_blank()
    )
```



## HQF and HQNF {.tabset .tabset-fade .tabset-pills}
### By MG {.tabset .tabset-fade .tabset-pills}
#### Main figure
```{r shap-phiyld-HQ-MG, eval=TRUE, echo=FALSE}
# Prepare the insert table:
d <- 
  dplyr::bind_rows(
    HQNF.shap %>%  
      dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
      # Convert yield from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
      dplyr::mutate(actual = actual*0.06725) %>%
      # Using descriptive names, so hence the quotes:
      dplyr::summarise(`No. fields` = n(), `Min Yield` = min(actual), `Max Yield` = max(actual), 
                       `Mean Yield` = mean(actual)) %>%
      dplyr::ungroup() %>%
      # Restrict display to 1 decimal place:
      dplyr::mutate(`Min Yield` = sprintf("%.1f", `Min Yield`),
                    `Max Yield` = sprintf("%.1f", `Max Yield`),
                    `Mean Yield` = sprintf("%.1f", `Mean Yield`)) %>%
      dplyr::mutate(fungicide = "Unsprayed") %>%
      dplyr::select(fungicide, everything()),
    
    HQF.shap %>%  
      dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
      # Convert yield from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
      dplyr::mutate(actual = actual*0.06725) %>%
      dplyr::summarise(`No. fields` = n(), `Min Yield` = min(actual), `Max Yield` = max(actual), 
                       `Mean Yield` = mean(actual)) %>%
      dplyr::ungroup() %>%
      dplyr::mutate(`Min Yield` = sprintf("%.1f", `Min Yield`),
                    `Max Yield` = sprintf("%.1f", `Max Yield`),
                    `Mean Yield` = sprintf("%.1f", `Mean Yield`)) %>%
      dplyr::mutate(fungicide = "Sprayed") %>%
      dplyr::select(fungicide, everything())
    ) %>% 
  # I want the rows labelled by fungicide use:
  tibble::column_to_rownames(var = "fungicide")
  

## All HQ fields, plot points by MG and fungicide
dplyr::bind_rows(
HQF.shap %>% 
  dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
  dplyr::mutate(mn = purrr::map_dbl(shap, purrr::pluck, "mean")) %>%
  dplyr::mutate(ylddiff = actual - mn) %>%
  dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
    purrr::pluck(.shap, "res") %>% 
    dplyr::filter(feature == "foliar.fungicide") %>%
    dplyr::pull(phi)})) %>% 
  dplyr::mutate(MG = purrr::map_chr(shap, function(.shap) {
    purrr::pluck(.shap, "res") %>% 
      dplyr::filter(feature == "MG.f") %>%
      dplyr::select(feature.value) %>%
      stringr::str_remove("MG.f=")})) %>%
  dplyr::mutate(fung = "Y") %>%
  dplyr::select(fung, ylddiff:MG)
,
HQNF.shap %>% 
  dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
  dplyr::mutate(mn = purrr::map_dbl(shap, purrr::pluck, "mean")) %>%
  dplyr::mutate(ylddiff = actual - mn) %>%
  dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
    purrr::pluck(.shap, "res") %>% 
      dplyr::filter(feature == "foliar.fungicide") %>%
      dplyr::pull(phi)})) %>% 
  dplyr::mutate(MG = purrr::map_chr(shap, function(.shap) {
    purrr::pluck(.shap, "res") %>% 
      dplyr::filter(feature == "MG.f") %>%
      dplyr::select(feature.value) %>%
      stringr::str_remove("MG.f=")})) %>%
  dplyr::mutate(fung = "N") %>%
  dplyr::select(fung, ylddiff:MG)
) %>%
  dplyr::mutate(fung = factor(fung, levels = c("N", "Y"), labels = c("Unsprayed", "Sprayed"))) %>%
  dplyr::mutate(MG = factor(MG, levels = c("0", "I", "II", "III", "IV"))) %>%
  # Convert yield from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
  dplyr::mutate(ylddiff = ylddiff*0.06725) %>%
  dplyr::mutate(phi = phi*0.06725) %>%
  ggplot(., aes(x = ylddiff, y = phi, colour = MG, shape = fung)) +
  geom_point(size = 2.0, alpha = 0.8) +
  scale_color_brewer(type = "qual", palette = "Set1", direction = 1, drop = FALSE) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = 2) +
  xlim(0, 2.5) +
  ylab("Phi value (t/ha)") +
  xlab("Single field predicted yield - mean predicted yield (t/ha)") +
  theme(axis.title.x = element_text(face = "bold", size = 12),
        axis.text.x  = element_text(size = 10, angle = 0),
        axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
        axis.text.y  = element_text(size = 10)) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "horizontal") +
  # override the transparency of the points for the legend:
  guides(shape = guide_legend(nrow = 1, title = "Fungicide", override.aes = list(alpha = 1)), 
         colour = guide_legend(nrow = 1, title = "Maturity group", override.aes = list(alpha = 1))) +
  # Use the rowhead argument to set the labels to non-italic bold:
  annotation_custom(gridExtra::tableGrob(d, 
                              theme = ttheme_default(base_size = 7,
                                                     rowhead = list(fg_params = list(col = "black", fontface = 2L)))), 
                    xmin = -0.2, xmax = 1.1, ymin = 0.3, ymax = 0.45)
```

#### Summary of the $\phi$ values
```{r shap-phiyld-HQ-MG-smry, eval=TRUE, echo=FALSE}
# GOAL: two-panel figure (sprayed and unsprayed). Each panel plots phi on x axis, MG on y axis. 
# Points: individual phi for each field, and large dot for the overall mean per MG.

# Extract the phi values and MG from the .shap objects:
d.phi <- 
  dplyr::bind_rows(
  HQF.shap %>% 
  dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
    purrr::pluck(.shap, "res") %>% 
    dplyr::filter(feature == "foliar.fungicide") %>%
    dplyr::pull(phi)})) %>% 
  dplyr::mutate(MG = purrr::map_chr(shap, function(.shap) {
    purrr::pluck(.shap, "res") %>% 
      dplyr::filter(feature == "MG.f") %>%
      dplyr::select(feature.value) %>%
      stringr::str_remove("MG.f=")})) %>%
  dplyr::mutate(fung = "Y") %>%
  dplyr::select(fung, MG, phi)
,
HQNF.shap %>% 
    dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
    purrr::pluck(.shap, "res") %>% 
      dplyr::filter(feature == "foliar.fungicide") %>%
      dplyr::pull(phi)})) %>% 
  dplyr::mutate(MG = purrr::map_chr(shap, function(.shap) {
    purrr::pluck(.shap, "res") %>% 
      dplyr::filter(feature == "MG.f") %>%
      dplyr::select(feature.value) %>%
      stringr::str_remove("MG.f=")})) %>%
  dplyr::mutate(fung = "N") %>%
  dplyr::select(fung, MG, phi)
) %>%
  dplyr::mutate(fung = factor(fung, levels = c("N", "Y"), labels = c("Unsprayed", "Sprayed"))) %>%
  dplyr::mutate(MG = factor(MG, levels = c("0", "I", "II", "III", "IV"))) %>%
  # Convert phi from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
  dplyr::mutate(phi = phi*0.06725) 

# Check the limits on phi:
# d.phi %>%
#   dplyr::group_by(fung) %>%
#   dplyr::summarise(min.phi = min(phi), max.phi = max(phi))


fxn2 <- function(.df, .fung, .ylab, my.title, LL, UL) {
  # Plot the mean phi per MG, jitter for the phi of the individual fields within MG:
  #
  # Args:
  #  .df = data frame with MG, foliar fungicide, phi for fungicide
  #  .fung = character string for fungicide ("Sprayed", "Unsprayed")
  #  .ylab = character string for the y-axis label
  #  my.title = character string for the plot title
  #  LL = lower limit for the phi axis
  #  UL = upper limit for the phi axis
  #
  # Returns:
  #  plot of the predicted yield or phi for fungicide for individual fields in each TED, plus the mean
  #
  smry <- .df %>%
    dplyr::filter(fung == .fung) %>%
    dplyr::select(phi) %>%
    dplyr::summarise(mn = mean(phi)) %>%
    dplyr::pull(mn)
    
  
  .df %>%
  dplyr::filter(fung == .fung) %>%
  ggplot(., aes(x = MG, y = phi, colour = MG)) +
  coord_flip() +
  geom_hline(aes(yintercept = smry), color = "gray70", size = 0.6) +
  geom_jitter(position = position_jitter(seed = 2019, width = 0.1), size = 2, alpha = 0.25) +
  stat_summary(fun.y = "mean", geom = "point", size = 5) +
  scale_color_brewer(type = "qual", palette = "Set1", direction = 1, drop = FALSE) +
  scale_y_continuous(limits = c(LL, UL), expand = c(0.005, 0.005)) +
  labs(x = NULL, y = .ylab) +
  theme_bw() +
  ggtitle(my.title) +
  theme(
    legend.position = "none",
    axis.title.x = element_text(face = "bold", size = 12),
    axis.text.x  = element_text(size = 9, angle = 0),
    axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
    axis.text.y  = element_text(size = 9),
    panel.grid = element_blank(),
    plot.title = element_text(face = "bold")
    )
} # end function fxn2


h1 <- fxn2(.df = d.phi, .fung = "Sprayed", .ylab = "Phi (t/ha)", my.title = "Sprayed", LL = -0.1, UL = 0.5)  
h2 <- fxn2(.df = d.phi, .fung = "Unsprayed", .ylab = "Phi (t/ha)", my.title = "Unsprayed", LL = -0.1, UL = 0.5)  

grid.arrange(h1, h2, ncol = 1)
```

```{r shap-phiyld-HQ-MG-checks, eval=FALSE, echo=FALSE}
# Check the limits on phi:
d.phi %>%
  dplyr::group_by(fung) %>%
  dplyr::summarise(min.phi = min(phi), max.phi = max(phi), mean.phi = mean(phi))
```



### By doy
```{r shap-phiyld-HQ-doy, eval=TRUE, echo=FALSE}
dplyr::bind_rows(
  HQF.shap %>% 
    dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
    dplyr::mutate(mn = purrr::map_dbl(shap, purrr::pluck, "mean")) %>%
    dplyr::mutate(ylddiff = actual - mn) %>%
    dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
      purrr::pluck(.shap, "res") %>% 
        dplyr::filter(feature == "foliar.fungicide") %>%
        dplyr::pull(phi)})) %>% 
    dplyr::mutate(doy = purrr::map_dbl(shap, function(.shap) {
      purrr::pluck(.shap, "res") %>% 
        dplyr::filter(feature == "doy") %>%
        dplyr::select(feature.value) %>%
        stringr::str_remove(".*=") %>%
        as.numeric()})) %>%
    dplyr::mutate(fung = "Y") %>%
    dplyr::select(fung, ylddiff:doy)
  ,
  HQNF.shap %>% 
    dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
    dplyr::mutate(mn = purrr::map_dbl(shap, purrr::pluck, "mean")) %>%
    dplyr::mutate(ylddiff = actual - mn) %>%
    dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
      purrr::pluck(.shap, "res") %>% 
        dplyr::filter(feature == "foliar.fungicide") %>%
        dplyr::pull(phi)})) %>% 
    dplyr::mutate(doy = purrr::map_dbl(shap, function(.shap) {
      purrr::pluck(.shap, "res") %>% 
        dplyr::filter(feature == "doy") %>%
        dplyr::select(feature.value) %>%
        stringr::str_remove(".*=") %>%
        as.numeric()})) %>%
    dplyr::mutate(fung = "N") %>%
    dplyr::select(fung, ylddiff:doy)
) %>%
  dplyr::mutate(fung = factor(fung, levels = c("N", "Y"), labels = c("Unsprayed", "Sprayed"))) %>%
  # Convert yield from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
  dplyr::mutate(ylddiff = ylddiff*0.06725) %>%
  dplyr::mutate(phi = phi*0.06725) %>%
  ggplot(., aes(x = ylddiff, y = phi, colour = doy, shape = fung)) +
  geom_point(size = 2.0, alpha = 1.0) +
  scale_colour_distiller(palette = "Spectral") +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = 2) +
  xlim(0, 2.5) +
  ylab("Phi value (t/ha)") +
  xlab("Single field predicted yield - mean predicted yield (t/ha)") +
  theme(axis.title.x = element_text(face = "bold", size = 12),
        axis.text.x  = element_text(size = 10, angle = 0),
        axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
        axis.text.y  = element_text(size = 10)) +
  theme(legend.position = "right", legend.direction = "vertical", legend.box = "vertical") +
  labs(colour = "Sowing date", shape = "Fungicide")
```


### By GDD
```{r shap-phiyld-HQ-GDD, eval=TRUE, echo=FALSE}
dplyr::bind_rows(
  HQF.shap %>% 
    dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
    dplyr::mutate(mn = purrr::map_dbl(shap, purrr::pluck, "mean")) %>%
    dplyr::mutate(ylddiff = actual - mn) %>%
    dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
      purrr::pluck(.shap, "res") %>% 
        dplyr::filter(feature == "foliar.fungicide") %>%
        dplyr::pull(phi)})) %>% 
    dplyr::mutate(GDD = purrr::map_chr(shap, function(.shap) {
      purrr::pluck(.shap, "res") %>% 
        dplyr::filter(feature == "GDD") %>%
        dplyr::select(feature.value) %>%
        stringr::str_remove(".*=")})) %>%
    dplyr::mutate(fung = "Y") %>%
    dplyr::select(fung, ylddiff:GDD)
  ,
  HQNF.shap %>% 
    dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
    dplyr::mutate(mn = purrr::map_dbl(shap, purrr::pluck, "mean")) %>%
    dplyr::mutate(ylddiff = actual - mn) %>%
    dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
      purrr::pluck(.shap, "res") %>% 
        dplyr::filter(feature == "foliar.fungicide") %>%
        dplyr::pull(phi)})) %>% 
    dplyr::mutate(GDD = purrr::map_chr(shap, function(.shap) {
      purrr::pluck(.shap, "res") %>% 
        dplyr::filter(feature == "GDD") %>%
        dplyr::select(feature.value) %>%
        stringr::str_remove(".*=")})) %>%
    dplyr::mutate(fung = "N") %>%
    dplyr::select(fung, ylddiff:GDD)
) %>%
  dplyr::mutate(fung = factor(fung, levels = c("N", "Y"), labels = c("Unsprayed", "Sprayed"))) %>%
  dplyr::mutate(GDD = factor(GDD, levels = c("01", "02", "03", "04", "05"))) %>%
  # Convert yield from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
  dplyr::mutate(ylddiff = ylddiff*0.06725) %>%
  dplyr::mutate(phi = phi*0.06725) %>%
  ggplot(., aes(x = ylddiff, y = phi, colour = GDD, shape = fung)) +
  geom_point(size = 2) +
  # scale_color_brewer(type = "qual", palette = "Set1", direction = 1, drop = FALSE) +
  ggsci::scale_color_uchicago(palette = "dark", drop = FALSE, alpha = 0.8) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = 2) +
  xlim(0, 2.5) +
  ylab("Phi value (t/ha)") +
  xlab("Single field predicted yield - mean predicted yield (t/ha)") +
  theme(axis.title.x = element_text(face = "bold", size = 12),
        axis.text.x  = element_text(size = 10, angle = 0),
        axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
        axis.text.y  = element_text(size = 10)) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "horizontal") +
  # override the transparency of the points for the legend:
  guides(shape = guide_legend(nrow = 1, title = "Fungicide", override.aes = list(alpha = 1)), 
         colour = guide_legend(nrow = 1, title = "GDD", override.aes = list(alpha = 1)))
```


### Composite plot {.tabset .tabset-fade .tabset-pills}
#### Original
```{r ThreeFigCompositeVer1, eval=TRUE, echo=FALSE}
# Prepare the insert table:
d <- 
  dplyr::bind_rows(
    HQNF.shap %>%  
      dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
      # Convert yield from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
      dplyr::mutate(actual = actual*0.06725) %>%
      # Using descriptive names, so hence the quotes:
      dplyr::summarise(`No. fields` = n(), `Min Yield` = min(actual), `Max Yield` = max(actual), 
                       `Mean Yield` = mean(actual)) %>%
      dplyr::ungroup() %>%
      # Restrict display to 1 decimal place:
      dplyr::mutate(`Min Yield` = sprintf("%.1f", `Min Yield`),
                    `Max Yield` = sprintf("%.1f", `Max Yield`),
                    `Mean Yield` = sprintf("%.1f", `Mean Yield`)) %>%
      dplyr::mutate(fungicide = "Unsprayed") %>%
      dplyr::select(fungicide, everything()),
    
    HQF.shap %>%  
      dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
      # Convert yield from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
      dplyr::mutate(actual = actual*0.06725) %>%
      dplyr::summarise(`No. fields` = n(), `Min Yield` = min(actual), `Max Yield` = max(actual), 
                       `Mean Yield` = mean(actual)) %>%
      dplyr::ungroup() %>%
      dplyr::mutate(`Min Yield` = sprintf("%.1f", `Min Yield`),
                    `Max Yield` = sprintf("%.1f", `Max Yield`),
                    `Mean Yield` = sprintf("%.1f", `Mean Yield`)) %>%
      dplyr::mutate(fungicide = "Sprayed") %>%
      dplyr::select(fungicide, everything())
    ) %>% 
  # I want the rows labelled by fungicide use:
  tibble::column_to_rownames(var = "fungicide")

## Yield summary table:
# Use the rowhead argument to set the labels to non-italic bold:
t1 <- gridExtra::tableGrob(d, theme = ttheme_default(base_size = 9, rowhead = list(fg_params = list(col = "black", 
                                                                                              fontface = 2L))))
  
  
## By MG: All HQ fields, plot points by MG and fungicide
p1dat <-
  dplyr::bind_rows(
  HQF.shap %>% 
  dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
  dplyr::mutate(mn = purrr::map_dbl(shap, purrr::pluck, "mean")) %>%
  dplyr::mutate(ylddiff = actual - mn) %>%
  dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
    purrr::pluck(.shap, "res") %>% 
    dplyr::filter(feature == "foliar.fungicide") %>%
    dplyr::pull(phi)})) %>% 
  dplyr::mutate(MG = purrr::map_chr(shap, function(.shap) {
    purrr::pluck(.shap, "res") %>% 
      dplyr::filter(feature == "MG.f") %>%
      dplyr::select(feature.value) %>%
      stringr::str_remove("MG.f=")})) %>%
  dplyr::mutate(fung = "Y") %>%
  dplyr::select(fung, ylddiff:MG)
,
HQNF.shap %>% 
  dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
  dplyr::mutate(mn = purrr::map_dbl(shap, purrr::pluck, "mean")) %>%
  dplyr::mutate(ylddiff = actual - mn) %>%
  dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
    purrr::pluck(.shap, "res") %>% 
      dplyr::filter(feature == "foliar.fungicide") %>%
      dplyr::pull(phi)})) %>% 
  dplyr::mutate(MG = purrr::map_chr(shap, function(.shap) {
    purrr::pluck(.shap, "res") %>% 
      dplyr::filter(feature == "MG.f") %>%
      dplyr::select(feature.value) %>%
      stringr::str_remove("MG.f=")})) %>%
  dplyr::mutate(fung = "N") %>%
  dplyr::select(fung, ylddiff:MG)
) %>%
  dplyr::mutate(fung = factor(fung, levels = c("N", "Y"), labels = c("Unsprayed", "Sprayed"))) %>%
  dplyr::mutate(MG = factor(MG, levels = c("0", "I", "II", "III", "IV"))) %>%
  # Convert yield from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
  dplyr::mutate(ylddiff = ylddiff*0.06725) %>%
  dplyr::mutate(phi = phi*0.06725) 

# ORIGINAL:
p1 <-
  p1dat %>%
  ggplot(., aes(x = ylddiff, y = phi, colour = MG, shape = fung)) +
  geom_point(size = 2.0, alpha = 0.8) +
  scale_color_brewer(type = "qual", palette = "Set1", direction = 1, drop = FALSE) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = 2) +
  xlim(0, 2.5) +
  ylab(NULL) +
  xlab(NULL) +
  theme(axis.text.x  = element_text(size = 10, angle = 0),
        axis.text.y  = element_text(size = 10)) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "vertical") +
  # override the transparency of the points for the legend:
  guides(shape = FALSE,
         colour = guide_legend(nrow = 1, title = "Maturity group", override.aes = list(alpha = 1))) +
  ggtitle("a") +
  theme(plot.title = element_text(face = "bold", size = 12))


## By doy
p2dat <- 
  dplyr::bind_rows(
  HQF.shap %>% 
    dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
    dplyr::mutate(mn = purrr::map_dbl(shap, purrr::pluck, "mean")) %>%
    dplyr::mutate(ylddiff = actual - mn) %>%
    dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
      purrr::pluck(.shap, "res") %>% 
        dplyr::filter(feature == "foliar.fungicide") %>%
        dplyr::pull(phi)})) %>% 
    dplyr::mutate(doy = purrr::map_dbl(shap, function(.shap) {
      purrr::pluck(.shap, "res") %>% 
        dplyr::filter(feature == "doy") %>%
        dplyr::select(feature.value) %>%
        stringr::str_remove(".*=") %>%
        as.numeric()})) %>%
    dplyr::mutate(fung = "Y") %>%
    dplyr::select(fung, ylddiff:doy)
  ,
  HQNF.shap %>% 
    dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
    dplyr::mutate(mn = purrr::map_dbl(shap, purrr::pluck, "mean")) %>%
    dplyr::mutate(ylddiff = actual - mn) %>%
    dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
      purrr::pluck(.shap, "res") %>% 
        dplyr::filter(feature == "foliar.fungicide") %>%
        dplyr::pull(phi)})) %>% 
    dplyr::mutate(doy = purrr::map_dbl(shap, function(.shap) {
      purrr::pluck(.shap, "res") %>% 
        dplyr::filter(feature == "doy") %>%
        dplyr::select(feature.value) %>%
        stringr::str_remove(".*=") %>%
        as.numeric()})) %>%
    dplyr::mutate(fung = "N") %>%
    dplyr::select(fung, ylddiff:doy)
) %>%
  dplyr::mutate(fung = factor(fung, levels = c("N", "Y"), labels = c("Unsprayed", "Sprayed"))) %>%
  # Convert yield from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
  dplyr::mutate(ylddiff = ylddiff*0.06725) %>%
  dplyr::mutate(phi = phi*0.06725) 

# ORIGINAL p2:
p2 <-
  p2dat %>%
  ggplot(., aes(x = ylddiff, y = phi, colour = doy, shape = fung)) +
  geom_point(size = 2.0, alpha = 1.0) +
  scale_colour_distiller(palette = "Spectral") +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = 2) +
  xlim(0, 2.5) +
  ylab(NULL) +
  xlab(NULL) +
  theme(axis.text.x  = element_text(size = 10, angle = 0),
        axis.text.y  = element_text(size = 10)) +
  theme(legend.position = "right", legend.direction = "vertical", legend.box = "vertical") +
  labs(colour = "Sowing date", shape = "Fungicide") +
  ggtitle("b") +
  theme(plot.title = element_text(face = "bold", size = 12))


## By GDD
p3dat <-
  dplyr::bind_rows(
  HQF.shap %>% 
    dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
    dplyr::mutate(mn = purrr::map_dbl(shap, purrr::pluck, "mean")) %>%
    dplyr::mutate(ylddiff = actual - mn) %>%
    dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
      purrr::pluck(.shap, "res") %>% 
        dplyr::filter(feature == "foliar.fungicide") %>%
        dplyr::pull(phi)})) %>% 
    dplyr::mutate(GDD = purrr::map_chr(shap, function(.shap) {
      purrr::pluck(.shap, "res") %>% 
        dplyr::filter(feature == "GDD") %>%
        dplyr::select(feature.value) %>%
        stringr::str_remove(".*=")})) %>%
    dplyr::mutate(fung = "Y") %>%
    dplyr::select(fung, ylddiff:GDD)
  ,
  HQNF.shap %>% 
    dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
    dplyr::mutate(mn = purrr::map_dbl(shap, purrr::pluck, "mean")) %>%
    dplyr::mutate(ylddiff = actual - mn) %>%
    dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
      purrr::pluck(.shap, "res") %>% 
        dplyr::filter(feature == "foliar.fungicide") %>%
        dplyr::pull(phi)})) %>% 
    dplyr::mutate(GDD = purrr::map_chr(shap, function(.shap) {
      purrr::pluck(.shap, "res") %>% 
        dplyr::filter(feature == "GDD") %>%
        dplyr::select(feature.value) %>%
        stringr::str_remove(".*=")})) %>%
    dplyr::mutate(fung = "N") %>%
    dplyr::select(fung, ylddiff:GDD)
) %>%
  dplyr::mutate(fung = factor(fung, levels = c("N", "Y"), labels = c("Unsprayed", "Sprayed"))) %>%
  dplyr::mutate(GDD = factor(GDD, levels = c("01", "02", "03", "04", "05"))) %>%
  # Convert yield from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
  dplyr::mutate(ylddiff = ylddiff*0.06725) %>%
  dplyr::mutate(phi = phi*0.06725) 


# ORIGINAL:
p3 <-
  p3dat %>%
  ggplot(., aes(x = ylddiff, y = phi, colour = GDD, shape = fung)) +
  geom_point(size = 2) +
  # scale_color_brewer(type = "qual", palette = "Set1", direction = 1, drop = FALSE) +
  ggsci::scale_color_uchicago(palette = "dark", drop = FALSE, alpha = 0.8) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = 2) +
  xlim(0, 2.5) +
  ylab(NULL) +
  xlab(NULL) +
  theme(axis.text.x  = element_text(size = 10, angle = 0),
        axis.text.y  = element_text(size = 10)) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "vertical") +
  # override the transparency of the points for the legend:
  guides(shape = FALSE,
         colour = guide_legend(nrow = 1, title = "GDD", override.aes = list(alpha = 1))) +
  ggtitle("c") +
  theme(plot.title = element_text(face = "bold", size = 12))



# This was my original layout:
grid.arrange(p1, p2, p3, t1, ncol = 2,
             bottom = grid::textGrob("Single field predicted yield - mean predicted yield (t/ha)", 
                                     gp = grid::gpar(fontface = "bold", fontsize = 12)),
             left = grid::textGrob("Phi value (t/ha)", 
                                   gp = grid::gpar(fontface = "bold", fontsize = 12), rot = 90)
             )
```


#### Revised
<!-- Figure 5 -->
```{r ThreeFigCompositeVer2, eval=TRUE, echo=FALSE}
## p1 revised so that legend is on the right:
p1.r <-
  p1dat %>%
  ggplot(., aes(x = ylddiff, y = phi, colour = MG, shape = fung)) +
  geom_point(size = 2.0, alpha = 0.8) +
  scale_color_brewer(type = "qual", palette = "Set1", direction = 1, drop = FALSE) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = 2) +
  xlim(0, 2.5) +
  ylab(NULL) +
  xlab(NULL) +
  theme(axis.text.x  = element_text(size = 10, angle = 0),
        axis.text.y  = element_text(size = 10)) +
  theme(legend.position = "right", legend.direction = "vertical", legend.box = "vertical") +
  # override the transparency of the points for the legend:
  guides(shape = FALSE, 
         colour = guide_legend(title = "Maturity\ngroup", override.aes = list(alpha = 1))) +
  ggtitle("a") +
  theme(plot.title = element_text(face = "bold", size = 12))

### REVISION: want the continuous scale for doy, no legend for fungicide
# See this for ideas: https://stackoverflow.com/questions/44168996/how-to-create-a-continuous-legend-color-bar-style-for-scale-alpha
# But the key here was to remember that plotting is in layers, so can remove the fungicide legend last.
p2.r <-
  p2dat %>%
  ggplot(., aes(x = ylddiff, y = phi, colour = doy, shape = fung)) +
  geom_point(size = 2.0) +
  scale_colour_distiller(palette = "Spectral") +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = 2) +
  xlim(0, 2.5) +
  ylab(NULL) +
  xlab(NULL) +
  theme(axis.text.x  = element_text(size = 10, angle = 0),
        axis.text.y  = element_text(size = 10)) +
  theme(legend.position = "right", legend.direction = "vertical", legend.box = "vertical") +
  labs(colour = "Sowing\ndate") +
  guides(shape = FALSE) +
  ggtitle("b") +
  theme(plot.title = element_text(face = "bold", size = 12))

# REVISED: legend is placed on the right:
p3.r <-
  p3dat %>%
  ggplot(., aes(x = ylddiff, y = phi, colour = GDD, shape = fung)) +
  geom_point(size = 2) +
  # scale_color_brewer(type = "qual", palette = "Set1", direction = 1, drop = FALSE) +
  ggsci::scale_color_uchicago(palette = "dark", drop = FALSE, alpha = 0.8) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = 2) +
  xlim(0, 2.5) +
  ylab(NULL) +
  xlab(NULL) +
  theme(axis.text.x  = element_text(size = 10, angle = 0),
        axis.text.y  = element_text(size = 10)) +
  theme(legend.position = "right", legend.direction = "vertical", legend.box = "vertical") +
  # override the transparency of the points for the legend:
  guides(shape = FALSE, 
         colour = guide_legend(title = "GDD", override.aes = list(alpha = 1))) +
  ggtitle("c") +
  theme(plot.title = element_text(face = "bold", size = 12))

## Draw a plot with the fungicide (shape) legend:
p4 <-
  p3dat %>%
  ggplot(., aes(x = ylddiff, y = phi, colour = GDD, shape = fung)) +
  geom_point(size = 2) +
  ggsci::scale_color_uchicago(palette = "dark", drop = FALSE, alpha = 0.8) +
  theme_bw() +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "vertical") +
  # override the transparency of the points for the legend:
  guides(colour = FALSE, 
         shape = guide_legend(nrow = 1, title = "Fungicide", override.aes = list(alpha = 1)))

## Extract the shape legend:
leg1 <- gtable::gtable_filter(ggplot_gtable(ggplot_build(p4)), "guide-box") 

gs <- list(p1.r, p2.r, p3.r, leg1, t1) 
# Had to play around with the layout so that there was not too much empty space between the fungicide legend and the data table:
lay <- rbind(c(1, 2),
             c(1, 2),
             c(1, 2),
             c(3, 4),
             c(3, 5),
             c(3, NA))

# grid.arrange(grobs = gs, layout_matrix = lay,
#              bottom = grid::textGrob("Single field predicted yield - mean predicted yield (t/ha)", 
#                                      gp = grid::gpar(fontface = "bold", fontsize = 12)),
#              left = grid::textGrob("Phi value (t/ha)", 
#                                    gp = grid::gpar(fontface = "bold", fontsize = 12), rot = 90))


grid.arrange(grobs = gs, layout_matrix = lay,
             bottom = grid::textGrob("Single field predicted yield - mean predicted yield (t/ha)", 
                                     gp = grid::gpar(fontface = "bold", fontsize = 12)),
             left = grid::textGrob(expression(bolditalic("phi")~bold(" value (t/ha)")), 
                                   gp = grid::gpar(fontface = "bold", fontsize = 12), rot = 90))
```



# Economic analysis {.tabset .tabset-fade .tabset-pills}
* Fungicide applied to field
* Fix chemical and application costs ($61.90/ha)
* Specify soybean price received


## HYF in top 12 TEDs {.tabset .tabset-fade .tabset-pills}
### Single price point I {.tabset .tabset-fade .tabset-pills}
#### Figure
```{r Econ-Top12-Single-I-Fig, eval=TRUE, echo=FALSE}
fx <- function(.dat, .TED) {
  # for any one of HYF.shap, HYNF.shap, LYF.shap, LYNF.shap, iterate over sample_id in a TED and get the yield difference and phi values along with other information for plotting
  # Args:
  #  .dat = one of HYF.shap, HYNF.shap, LYF.shap, LYNF.shap
  #  .TED = a TED in one of the .shap files
  # Returns:
  #  a data frame of extracted phi and other components for each field
  #
  # Number of sample_id (fields) in a given TED:
  sl <- purrr::pluck(.dat, .TED, "sample_id") %>% length()
  
  # Iterate over all the sample_id in the TED:
  purrr::map_df(1:sl, function(.i) {
    purrr::pluck(.dat, .TED) %>% 
      dplyr::slice(.i) %>% 
      dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
      dplyr::mutate(mn = purrr::map_dbl(shap, purrr::pluck, "mean")) %>%
      dplyr::mutate(ylddiff = actual - mn) %>%
      dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "foliar.fungicide") %>%
          dplyr::pull(phi)})) %>%
      dplyr::mutate(fung = purrr::map_chr(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "foliar.fungicide") %>%
          dplyr::select(feature.value) %>%
          stringr::str_remove(".*=")})) %>%
      dplyr::mutate(TED = .TED) %>%
      dplyr::select(sample_id, TED, ylddiff, phi, fung)
  }
  )
}  # end fx

# Price = $350/t: this is on the low end of soybean prices
# Mean = $420/t
# High = $530/t

# NOTE: 1/26/2021: originally had done the graphic with price = $350/t, the low end. But thought it would be more realistic to do with the mean, so was redone with price = $420/t.

# Revised to reflect the price of 576.30 as of Jan 31 2021
# chem.cost comes from Kandel et al. (2016). Plant Health Progress. Based on statistics compiled for the corn fungicides project, chemical costs tend to be rather flat over time. 

soy.price <- 576.30
chem.cost <- 61.90

HY <-
  purrr::map_df(HYF.shap %>% names(), fx, .dat = HYF.shap) %>%
  dplyr::mutate(TED = factor(TED, levels = c("303603", "303703", "403603", "403703", "504803", "602303", "603503", "603603", "603703", "604503", "604603", "604803"))) %>%
  dplyr::select(-ylddiff, -fung) %>%
  # Convert phi from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
  dplyr::mutate(phi = phi*0.06725) %>%
  # Return (loss) on phi, given soybean price. In $/ha:
  dplyr::mutate(net.val = soy.price*phi) %>%
  # Net profit: substract cost of fungicide and application:
  dplyr::mutate(net.prof = net.val - chem.cost) %>%
  # Get the average net profit per TED:
  dplyr::group_by(TED) %>%
  dplyr::mutate(mean.TED = mean(net.prof)) %>%
  dplyr::ungroup()

g <-
  HY %>%
  dplyr::mutate(TED = fct_reorder(TED, -mean.TED)) %>%
  ggplot(., aes(x = TED, y = net.prof, color = TED)) +
  coord_flip() +
  scale_y_continuous(limits = c(-150, 150), expand = c(0.005, 0.005)) +
  scale_color_viridis_d(option = "D") +
  labs(x = "TED", y = "Return ($/ha)") +
  theme_bw() +
  theme(
    legend.position = "none",
    axis.title = element_text(face = "bold", size = 12),
    axis.title.x = element_text(face = "bold", size = 12),
    axis.text.x  = element_text(size = 9, angle = 0),
    axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
    axis.text.y  = element_text(size = 9),
    panel.grid = element_blank() 
    )


g +
  geom_segment(aes(x = TED, xend = TED, y = 0, yend = mean.TED), size = 0.8) + 
  geom_hline(aes(yintercept = 0), color = "gray70", size = 0.6) +
  geom_jitter(position = position_jitter(seed = 2019, width = 0.1), size = 2, alpha = 0.25) +
  stat_summary(fun.y = "mean", geom = "point", size = 5) +
  annotate("text", x = 1.0, y = -145, size = 2.8, color = "gray20", label = "Soybean price = $576.30/tonne", hjust = 0) +
  annotate("text", x = 1.5, y = -145, size = 2.8, color = "gray20", label = "Fungicide and application costs = $61.90/ha", hjust = 0) +
  annotate("text", x = 10.5, y = -35, size = 2.8, color = "gray20", label = "TED average") +
  geom_curve(aes(x = 10.5, y = -20.0, xend = 10.1, yend = 5.0),
             arrow = arrow(length = unit(0.07, "inch")), size = 0.4,
             color = "gray20", curvature = -0.3)
```


#### Tabular summary
The Figure shows fungicides overwhelmingly profitable, except in 4 TEDs (403603, 602303, 403703, 303603) in which individual fields were about as equally likely to realize a net profit or loss with respect to fungicide application.

* table the mean net profit (loss) for each TED

```{r Econ-Top12-Single-I-Table, eval=TRUE, echo=FALSE, results='markup'}
HY %>%
  dplyr::group_by(TED) %>%
  dplyr::summarise(n = n(), mean.profit = mean(net.prof)) %>%
  dplyr::arrange(mean.profit)
```

#### Confidence intervals
```{r Econ-Top12-Single-I-CI-Table, eval=TRUE, echo=FALSE, results='markup'}
# For reproducibilty:
set.seed(14092)

top12.ci <-
groupwiseMean(net.prof ~ TED,
              data   = HY,
              conf   = 0.95,
              digits = 4,
              R      = 10000,
              boot        = TRUE,
              traditional = FALSE,
              normal      = FALSE,
              basic       = FALSE,
              percentile  = FALSE,
              bca         = TRUE)

top12.ci %>%
  dplyr::arrange(Mean)
```

#### CI plot
<!-- Supplementary Figure S7 -->

```{r Econ-Top12-Single-I-CI-Fig, eval=TRUE, echo=FALSE}
top12.ci %>%
  # want higher importance to appear at the top of the plot:
  dplyr::arrange(desc(Mean)) %>%
  dplyr::mutate(TED = factor(TED, levels = .$TED)) %>%
  ggplot(., aes(y = TED, x = Mean)) +  
  # geom_segment(aes(y = TED, yend = TED, x = Bca.lower, xend = Bca.upper), size = 1.5, color = "darkslategrey") +
  # Want to maintain the same color scheme for TEDs throughout the series of graphics:
  geom_segment(aes(y = TED, yend = TED, x = Bca.lower, xend = Bca.upper, colour = TED), size = 1.5) +
  geom_point(aes(colour = TED), size = 4) +
  scale_color_viridis_d(option = "D") +
  theme_bw() +
  scale_x_continuous(name = "Return ($/ha)") + 
  scale_y_discrete(name = "TED") +
  theme(legend.position = "none") +
  theme(axis.title.x = element_text(face = "bold", size = 13)) + 
  theme(axis.title.y = element_text(face = "bold", size = 13)) +
  theme(axis.text.x  = element_text(size = 10, angle = 0)) +
  theme(axis.text.y  = element_text(size = 10))
```


### Single price point II
<!-- Figure 6 -->

* Different shapes for the points representing year

```{r Econ-Top12-Single-II-Fig, eval=TRUE, echo=FALSE}
# Paul requested a way to represent `year` in the graphic...
# FIRST: run the code in chunk `shap-Comparisons-Top12-HYF-HYNF`

# Price = $350/t: this is on the low end of soybean prices
# Mean = $420/t
# High = $530/t

soy.price <- 576.30
chem.cost <- 61.90

HY <-
  purrr::map_df(HYF.shap %>% names(), fx, .dat = HYF.shap) %>%
  dplyr::mutate(TED = factor(TED, levels = c("303603", "303703", "403603", "403703", "504803", "602303", "603503", "603603", "603703", "604503", "604603", "604803"))) %>%
  dplyr::select(-ylddiff, -fung) %>%
  # Convert yield from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
  dplyr::mutate(phi = phi*0.06725) %>%
  # Return (loss) on phi, given soybean price. In $/ha:
  dplyr::mutate(net.val = soy.price*phi) %>%
  # Net profit: substract cost of fungicide and application:
  dplyr::mutate(net.prof = net.val - chem.cost) %>%
  # Get the average net profit per TED:
  dplyr::group_by(TED) %>%
  dplyr::mutate(mean.TED = mean(net.prof)) %>%
  dplyr::ungroup()

# The sample_id values:
sample_id <- HY %>% dplyr::pull(sample_id)
  
# Get the corresponding order numbers:
order <- 
  dat %>%
  tibble::rowid_to_column() %>%
  dplyr::filter(rowid %in% sample_id) %>%
  dplyr::rename(sample_id = rowid) %>%
  dplyr::select(sample_id, order)

# Update HY with the order variable:
HY <-
  dplyr::left_join(HY, order, by = "sample_id") %>%
  # Use the order values to get the associated year for these fields:
  dplyr::left_join(., dat %>% dplyr::select(order, year), by = "order") %>%
  dplyr::select(-sample_id)


# Plot ... includes different shapes for year
g <-
  HY %>%
  dplyr::mutate(TED = fct_reorder(TED, -mean.TED)) %>%
  ggplot(., aes(x = TED, y = net.prof, color = TED, shape = factor(year))) +
  coord_flip() +
  scale_y_continuous(limits = c(-150, 150), expand = c(0.005, 0.005)) +
  scale_color_viridis_d(option = "D") +
  scale_shape_manual(values = c(15, 16, 17)) +
  labs(x = "TED", y = "Return ($/ha)") +
  theme_bw() +
  theme(
    axis.title = element_text(face = "bold", size = 12),
    axis.title.x = element_text(face = "bold", size = 12),
    axis.text.x  = element_text(size = 9, angle = 0),
    axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
    axis.text.y  = element_text(size = 9),
    panel.grid = element_blank() 
    ) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "vertical") +
  # override the transparency of the points for the legend:
  guides(colour = FALSE, 
         shape = guide_legend(nrow = 1, title = "Year", override.aes = list(alpha = 1)))


g +
  geom_segment(aes(x = TED, xend = TED, y = 0, yend = mean.TED), size = 0.8) + 
  geom_hline(aes(yintercept = 0), color = "gray70", size = 0.6) +
  geom_jitter(position = position_jitter(seed = 2019, width = 0.1), size = 2, alpha = 0.25) +
  # Specify the aesthetics and override so that you don't get separate points for year:
  stat_summary(aes(x = TED, y = net.prof, color = TED), fun.y = "mean", geom = "point", size = 5, inherit.aes = FALSE) +
  annotate("text", x = 1.0, y = -145, size = 2.8, color = "gray20", label = "Soybean price = $576.30/tonne", hjust = 0) +
  annotate("text", x = 1.5, y = -145, size = 2.8, color = "gray20", label = "Fungicide and application costs = $61.90/ha", hjust = 0) +
  annotate("text", x = 10.5, y = -35, size = 2.8, color = "gray20", label = "TED average") +
  geom_curve(aes(x = 10.5, y = -20.0, xend = 10.1, yend = 5.0),
             arrow = arrow(length = unit(0.07, "inch")), size = 0.4,
             color = "gray20", curvature = -0.3)
```


### Multiple price points
```{r Econ-Top12-Multiple-Functions, eval=TRUE, echo=FALSE}
roi <- function(.soyprice, .chemcost = 61.90, .yl = -150, .yu = 150, my.title, .pricelabel) {
  # A function to plot the return on the yield increase realized by a fungicide, after accounting for application and chemical costs
  # Args:
  #  .soyprice = soybean price received in $/tonne
  #  .chemcost = chemical and application costs ($/ha)
  #  .yl = lower limit on the y-axis
  #  .yu = upper limit on the y-axis
  #  my.title = title (label) for the plot
  #  .pricelabel = string for adding an annotation on the soybean price received
  # Returns:
  #  a plot of the mean return per ($/ha) as well as a jitter of the points for the individual fields
  #
  HY <-
  purrr::map_df(HYF.shap %>% names(), fx, .dat = HYF.shap) %>%
  dplyr::mutate(TED = factor(TED, levels = c("303603", "303703", "403603", "403703", "504803", "602303", "603503", "603603", "603703", "604503", "604603", "604803"))) %>%
  dplyr::select(-ylddiff, -fung) %>%
  # Convert yield from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
  dplyr::mutate(phi = phi*0.06725) %>%
  # Return (loss) on phi, given soybean price. In $/ha:
  dplyr::mutate(net.val = .soyprice*phi) %>%
  # Net profit: substract cost of fungicide and application:
  dplyr::mutate(net.prof = net.val - .chemcost) %>%
  # Get the average net profit per TED:
  dplyr::group_by(TED) %>%
  dplyr::mutate(mean.TED = mean(net.prof)) %>%
  dplyr::ungroup()
  
  # Plot ...
  g <-
  HY %>%
  dplyr::mutate(TED = fct_reorder(TED, -mean.TED)) %>%
  ggplot(., aes(x = TED, y = net.prof, color = TED)) +
  coord_flip() +
  scale_y_continuous(limits = c(.yl, .yu), expand = c(0.005, 0.005)) +
  scale_color_viridis_d(option = "D") +
  labs(x = NULL, y = NULL) +
  theme_bw() +
  theme(
    legend.position = "none",
    axis.text.x  = element_text(size = 9, angle = 0),
    axis.text.y  = element_text(size = 7),
    panel.grid = element_blank()) +
    ggtitle(my.title) +
    theme(plot.title = element_text(face = "bold"))
  
  g +
  geom_segment(aes(x = TED, xend = TED, y = 0, yend = mean.TED), size = 0.8) + 
  geom_hline(aes(yintercept = 0), color = "gray70", size = 0.6) +
  geom_jitter(position = position_jitter(seed = 2019, width = 0.1), size = 2, alpha = 0.25) +
  stat_summary(fun.y = "mean", geom = "point", size = 5) +
  annotate("text", x = 2.0, y = -145, size = 2.8, color = "gray20", label = .pricelabel, hjust = 0)
  }  # end function roi
```


<!-- Supplementary Figure S9 -->
```{r Econ-Top12-Multiple-Fig, eval=TRUE, echo=FALSE, fig.height=8.0}
# Set width to 600, Height to 650
# A multi-component plot
p1 <- roi(.soyprice = 350, .chemcost = 61.90, my.title = "a", .pricelabel = "$350/tonne")

p2 <- roi(.soyprice = 400, .chemcost = 61.90, my.title = "b", .pricelabel = "$400/tonne")

p3 <- roi(.soyprice = 450, .chemcost = 61.90, my.title = "c", .pricelabel = "$450/tonne")

p4 <- roi(.soyprice = 500, .chemcost = 61.90, my.title = "d", .pricelabel = "$500/tonne")

p5 <- roi(.soyprice = 550, .chemcost = 61.90, my.title = "e", .pricelabel = "$550/tonne")

p6 <- roi(.soyprice = 600, .chemcost = 61.90, my.title = "f", .pricelabel = "$600/tonne")

grid.arrange(p1, p2, p3, p4, p5, p6, ncol = 2,
             bottom = grid::textGrob("Return ($/ha)", 
                                     gp = grid::gpar(fontface = "bold", fontsize = 12)),
             left = grid::textGrob("TED", 
                                   gp = grid::gpar(fontface = "bold", fontsize = 12), rot = 90)
             )
```


## AllHYF and AllLYF {.tabset .tabset-fade .tabset-pills}
The economic return due to fungicide on the 100 highest-yielding fields and the 100 lowest-yielding fields in the dataset, all fields having been sprayed.

```{r Econ-All-Functions, eval=TRUE, echo=FALSE}
# Define a helper function:
fxa <- function(.dat, .yldenv) {
  # Extract the phi values from one of the Allxx.shap objects.
  # Args:
  #  .dat = one of AllHYF.shap, AllHYNF.shap, AllLYF.shap, AllLYNF.shap
  #  .yldenv = character string for best- or worst-yielding fields ("Low", "High")
  # Returns:
  #  a data frame of the extracted values
  #
  # Iterate over all the sample_id (there are 100 fields in each of the `All` groups:
  purrr::map_df(1:100, function(.i) {
      .dat %>%
      dplyr::slice(.i) %>% 
      dplyr::mutate(actual = purrr::map_dbl(shap, purrr::pluck, "actual")) %>%
      dplyr::mutate(mn = purrr::map_dbl(shap, purrr::pluck, "mean")) %>%
      dplyr::mutate(ylddiff = actual - mn) %>%
      dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "foliar.fungicide") %>%
          dplyr::pull(phi)})) %>%
      dplyr::mutate(fung = purrr::map_chr(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "foliar.fungicide") %>%
          dplyr::select(feature.value) %>%
          stringr::str_remove(".*=")})) %>%
      dplyr::mutate(yldenv = .yldenv) %>%
      dplyr::select(sample_id, ylddiff, phi, fung, yldenv)
  }
  )
}  # end fxa

# Define a function targeted to extracting the data from AllHYF.shap, and estimating the roi. 
roi2 <- function(.soyprice, .chemcost = 61.90, .yl = -150, .yu = 150, my.title, .pricelabel, .xlab = NULL, .ylab = NULL) {
  # A function to plot the return on the yield increase realized by a fungicide, after accounting for application and chemical costs
  # Args:
  #  .soyprice = soybean price received in $/tonne
  #  .chemcost = chemical and application costs ($/ha)
  #  .yl = lower limit on the y-axis
  #  .yu = upper limit on the y-axis
  #  my.title = title (label) for the plot
  #  .pricelabel = string for adding an annotation on the soybean price received
  # Returns:
  #  a plot of the mean return per ($/ha) as well as a jitter of the points for the individual fields
  #
  # Prep the data:
  x <-
  dplyr::bind_rows(fxa(.dat = AllHYF.shap, .yldenv = "Sprayed (HY)"),
                   fxa(.dat = AllLYF.shap, .yldenv = "Sprayed (LY)")) %>%
  # Convert phi from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
  dplyr::mutate(phi = phi*0.06725) %>%
  # Return (loss) on phi, given soybean price. In $/ha:
  dplyr::mutate(net.val = .soyprice*phi) %>%
  # Net profit: substract cost of fungicide and application:
  dplyr::mutate(net.prof = net.val - .chemcost) 
  
  # Plot ...
  x %>%
  ggplot(., aes(x = yldenv, y = net.prof, colour = yldenv, shape = yldenv)) +
  coord_flip() +
  geom_jitter(position = position_jitter(seed = 2019, width = 0.1), size = 2, alpha = 0.25) +
  stat_summary(fun.y = "mean", geom = "point", size = 5) +
  # Based on RColorbrewer qualitative set 1:
  scale_color_manual(values = c("#377eb8", "#ff7f00")) + 
  scale_y_continuous(limits = c(.yl, .yu), expand = c(0.005, 0.005)) +
  labs(x = .xlab, y = .ylab) +
  theme_bw() +
  geom_hline(aes(yintercept = 0), color = "gray70", size = 0.6) +
  theme(
    legend.position = "none",
    axis.title.x = element_text(face = "bold", size = 13),
    axis.text.x  = element_text(size = 11, angle = 0),
    axis.title.y = element_text(size = 13, angle = 90, face = "bold"),
    axis.text.y  = element_text(size = 11),
    panel.grid = element_blank()
    ) +
  annotate("text", x = 0.5, y = -125, size = 3.0, color = "gray20", label = .pricelabel, hjust = 0) +
    ggtitle(my.title) +
    theme(plot.title = element_text(face = "bold"))
  }  # end function roi2
```

### Single price point {.tabset .tabset-fade .tabset-pills}
* Price = US576.30/tonne

#### Figure 
<!-- Supplementary Figure S8 -->
```{r Econ-All-Single-Price, eval=TRUE, echo=FALSE}
roi2(.soyprice = 576.30, .chemcost = 61.90, .yl = -150, .yu = 210, my.title = NULL, .pricelabel = "Price = $576.30/tonne", .ylab = "Return ($/ha)")
```

#### Table
```{r Econ-All-Single-Price-Table, eval=TRUE, echo=FALSE, results='markup'}
soy.price <- 576.30
chem.cost <- 61.90

# Prep the data:
z <- 
  dplyr::bind_rows(fxa(.dat = AllHYF.shap, .yldenv = "Sprayed (HY)"),
                   fxa(.dat = AllLYF.shap, .yldenv = "Sprayed (LY)")) %>%
  # Convert phi from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
  dplyr::mutate(phi = phi*0.06725) %>%
  # Return (loss) on phi, given soybean price. In $/ha:
  dplyr::mutate(net.val = soy.price*phi) %>%
  # Net profit: substract cost of fungicide and application:
  dplyr::mutate(net.prof = net.val - chem.cost) %>%
  dplyr::select(yldenv, net.prof)

# The mean profitability by cohort:
z %>%
  dplyr::group_by(yldenv) %>%
  dplyr::summarise(NetProfit = mean(net.prof))
```

#### Confidence interval
Bias Corrected and Accelerated (BCa) bootstrap Confidence Intervals for the mean profitability

```{r Econ-All-Single-Price-CI, eval=TRUE, echo=FALSE, results='markup'}
# confidence interval for mean profitability
# library(rcompanion)
set.seed(14092)

all.ci <-
groupwiseMean(net.prof ~ yldenv,
              data   = z,
              conf   = 0.95,
              digits = 4,
              R      = 10000,
              boot        = TRUE,
              traditional = FALSE,
              normal      = FALSE,
              basic       = FALSE,
              percentile  = FALSE,
              bca         = TRUE)

all.ci
```


### Multiple price points
* A range of prices

<!-- Supplementary Figure S10 -->
```{r Econ-All-Multiple-Prices, eval=TRUE, echo=FALSE, fig.height=8.0}
# Set width = 743, height = 650
p1 <- roi2(.soyprice = 350, .chemcost = 61.90, .yl = -150, .yu = 210, my.title = "a", .pricelabel = "$350/tonne")
p2 <- roi2(.soyprice = 400, .chemcost = 61.90, .yl = -150, .yu = 210, my.title = "b", .pricelabel = "$400/tonne")
p3 <- roi2(.soyprice = 450, .chemcost = 61.90, .yl = -150, .yu = 210, my.title = "c", .pricelabel = "$450/tonne")
p4 <- roi2(.soyprice = 500, .chemcost = 61.90, .yl = -150, .yu = 210, my.title = "d", .pricelabel = "$500/tonne")
p5 <- roi2(.soyprice = 550, .chemcost = 61.90, .yl = -150, .yu = 210, my.title = "e", .pricelabel = "$550/tonne")
p6 <- roi2(.soyprice = 600, .chemcost = 61.90, .yl = -150, .yu = 210, my.title = "f", .pricelabel = "$600/tonne")

grid.arrange(p1, p2, p3, p4, p5, p6, ncol = 2,
             bottom = grid::textGrob("Return ($/ha)", 
                                     gp = grid::gpar(fontface = "bold", fontsize = 12))
             )
```



## HQF and HQNF {.tabset .tabset-fade .tabset-pills}
* The set of fields in the 90th percentile for yield
* Must be careful here: for unsprayed fields, chem.cost = 0

```{r Econ-HQ-Functions, eval=TRUE, echo=FALSE}
roi.hq.mg <- function(.price, .chemcost = 61.90, .ll = -150, .ul = 210, .xlab = NULL, .ylab = NULL, .maintitle = NULL, .pricelabel = "foo", .ann.x = 0.7, .ann.y = -130) {
  # Plots the roi for HQF fields by MG and fungicide use
  # Args:
  #  .price =  soybean price ($/tonne)
  #  .chemcost = fungicide and application costs ($/ha)
  #  .ll = lower limit on the y-axis
  #  .ul = upper limit on the y-axis
  #  .xlab = x-axis label (be aware we use coord_flip in the plot)
  #  .ylab = y-axis label
  #  .maintitle = main title for the plot
  #  .pricelabel = text label for the soybean price
  #  .ann.x = x-axis coord for the price label
  #  .ann.y = y-axis coord for the price label
  #
  # Returns:
  #  a plot of the ROI for the different MGs in the HQF set of fields
  #
  # Prepare the data:
  hq.mg <-
    dplyr::bind_rows(
      HQF.shap %>% 
        dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
          purrr::pluck(.shap, "res") %>% 
            dplyr::filter(feature == "foliar.fungicide") %>%
            dplyr::pull(phi)})) %>% 
        dplyr::mutate(MG = purrr::map_chr(shap, function(.shap) {
          purrr::pluck(.shap, "res") %>% 
            dplyr::filter(feature == "MG.f") %>%
            dplyr::select(feature.value) %>%
            stringr::str_remove("MG.f=")})) %>%
        dplyr::mutate(fung = "Y") %>%
        dplyr::select(fung, phi, MG) %>%
        # Convert phi from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
        dplyr::mutate(phi = phi*0.06725) %>%
        # Return (loss) on phi, given soybean price. In $/ha:
        dplyr::mutate(net.val = .price*phi) %>%
        # Net profit: substract cost of fungicide and application:
        dplyr::mutate(net.prof = net.val - .chemcost)
      ,
      HQNF.shap %>% 
        dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
          purrr::pluck(.shap, "res") %>% 
            dplyr::filter(feature == "foliar.fungicide") %>%
            dplyr::pull(phi)})) %>% 
        dplyr::mutate(MG = purrr::map_chr(shap, function(.shap) {
          purrr::pluck(.shap, "res") %>% 
            dplyr::filter(feature == "MG.f") %>%
            dplyr::select(feature.value) %>%
            stringr::str_remove("MG.f=")})) %>%
        dplyr::mutate(fung = "N") %>%
        dplyr::select(fung, phi, MG) %>%
        # Convert phi from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
        dplyr::mutate(phi = phi*0.06725) %>%
        # Return (loss) on phi, given soybean price. In $/ha:
        dplyr::mutate(net.val = .price*phi) %>%
        # Net profit: substract cost of fungicide and application (zero for unsprayed fields):
        dplyr::mutate(net.prof = net.val - 0)
      ) %>%
    dplyr::mutate(fung = factor(fung, levels = c("N", "Y"), labels = c("Unsprayed", "Sprayed"))) %>%
    dplyr::mutate(MG = factor(MG, levels = c("0", "I", "II", "III", "IV"))) 
  
    
  # Plot ...
  hq.mg %>%
    ggplot(., aes(x = MG, y = net.prof, colour = MG, shape = fung)) +
    coord_flip() +
    geom_jitter(position = position_jitter(seed = 2019, width = 0.1), size = 2, alpha = 0.25) +
    stat_summary(fun.y = "mean", geom = "point", size = 5) +
    # Based on RColorbrewer qualitative set 1:
    scale_color_brewer(type = "qual", palette = "Set1", direction = 1, drop = FALSE) +
    scale_y_continuous(limits = c(.ll, .ul), expand = c(0.005, 0.005)) +
    labs(x = .xlab, y = .ylab) +
    theme_bw() +
    geom_hline(aes(yintercept = 0), color = "gray70", size = 0.6) +
    theme(
      legend.position = "bottom", legend.direction = "horizontal", legend.box = "vertical",
      axis.title.x = element_text(face = "bold", size = 13),
      axis.text.x  = element_text(size = 10, angle = 0),
      axis.title.y = element_text(size = 13, angle = 90, face = "bold"),
      axis.text.y  = element_text(size = 10),
      panel.grid = element_blank()
      ) +
    guides(colour = FALSE, shape = FALSE) +
    annotate("text", x = .ann.x, y = .ann.y, size = 2.5, color = "gray20", label = .pricelabel, hjust = 0) +
    ggtitle(.maintitle) +
    theme(plot.title = element_text(face = "bold", size = 12))
  } # end function roi.hq.mg

# Example of use:
# roi.hq.mg(.price = 576.30, .chemcost = 61.90, .ll = -150, .ul = 210, .xlab = NULL, .ylab = NULL, .maintitle = NULL)

roi.hq.doy <- function(.price, .chemcost = 61.90, .ll = -150, .ul = 210, .xlab = NULL, .ylab = NULL, .maintitle = NULL) {
  # Prep the data:
  hq.doy <- 
    dplyr::bind_rows(
      HQF.shap %>% 
        dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
          purrr::pluck(.shap, "res") %>% 
            dplyr::filter(feature == "foliar.fungicide") %>%
            dplyr::pull(phi)})) %>% 
        dplyr::mutate(doy = purrr::map_dbl(shap, function(.shap) {
          purrr::pluck(.shap, "res") %>% 
            dplyr::filter(feature == "doy") %>%
            dplyr::select(feature.value) %>%
            stringr::str_remove(".*=") %>%
            as.numeric()})) %>%
        dplyr::mutate(fung = "Y") %>%
        dplyr::select(fung, phi, doy) %>%
        # Convert from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
        dplyr::mutate(phi = phi*0.06725) %>%
        # Return (loss) on phi, given soybean price. In $/ha:
        dplyr::mutate(net.val = .price*phi) %>%
        # Net profit: substract cost of fungicide and application:
        dplyr::mutate(net.prof = net.val - .chemcost)
      ,
      HQNF.shap %>% 
        dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
          purrr::pluck(.shap, "res") %>% 
            dplyr::filter(feature == "foliar.fungicide") %>%
            dplyr::pull(phi)})) %>% 
        dplyr::mutate(doy = purrr::map_dbl(shap, function(.shap) {
          purrr::pluck(.shap, "res") %>% 
            dplyr::filter(feature == "doy") %>%
            dplyr::select(feature.value) %>%
            stringr::str_remove(".*=") %>%
            as.numeric()})) %>%
        dplyr::mutate(fung = "N") %>%
        dplyr::select(fung, phi, doy) %>%
        # Convert from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
        dplyr::mutate(phi = phi*0.06725) %>%
        # Return (loss) on phi, given soybean price. In $/ha:
        dplyr::mutate(net.val = .price*phi) %>%
        # Net profit: substract cost of fungicide and application:
        dplyr::mutate(net.prof = net.val - 0) 
      ) %>%
    dplyr::mutate(fung = factor(fung, levels = c("N", "Y"), labels = c("Unsprayed", "Sprayed")))
    
  
  # Plot ...  
  hq.doy %>%
    ggplot(., aes(x = net.prof, y = doy, colour = doy, shape = fung)) +
    geom_point(size = 2.0) +
    scale_colour_distiller(palette = "Spectral") +
    scale_x_continuous(limits = c(.ll, .ul), expand = c(0.005, 0.005)) +
    labs(x = .xlab, y = .ylab) +
    theme_bw() +
    geom_vline(aes(xintercept = 0), color = "gray70", size = 0.6) +
    theme(axis.title.x = element_text(face = "bold", size = 13),
          axis.text.x  = element_text(size = 10, angle = 0),
          axis.title.y = element_text(face = "bold", size = 13, angle = 90),
          axis.text.y  = element_text(size = 10)) +
    theme(legend.position = "right", legend.direction = "vertical", legend.box = "vertical") +
    labs(colour = "Sowing\ndate") +
    guides(shape = FALSE) +
    ggtitle(.maintitle) +
    theme(plot.title = element_text(face = "bold", size = 12))
} # end function roi.hq.doy


roi.hq.gdd <- function(.price, .chemcost = 61.90, .ll = -150, .ul = 210, .xlab = NULL, .ylab = NULL, .maintitle = NULL, .pricelabel = "foo", .ann.x = 0.7, .ann.y = -130) {
  # Plots the roi for HQF fields by GDD and fungicide use
  # Args:
  #  .price =  soybean price ($/tonne)
  #  .chemcost = fungicide and application costs ($/ha)
  #  .ll = lower limit on the y-axis
  #  .ul = upper limit on the y-axis
  #  .xlab = x-axis label (be aware we use coord_flip in the plot)
  #  .ylab = y-axis label
  #  .maintitle = main title for the plot
  #  .pricelabel = text label for the soybean price
  #  .ann.x = x-axis coord for price label placement
  #  .ann.y = y-axis coord for price label placement
  #
  # Returns:
  #  a plot of the ROI for the different MGs in the HQF set of fields
  #
  # Prepare the data:
  hq.gdd <-
    dplyr::bind_rows(
      HQF.shap %>% 
        dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
          purrr::pluck(.shap, "res") %>% 
            dplyr::filter(feature == "foliar.fungicide") %>%
            dplyr::pull(phi)})) %>% 
        dplyr::mutate(GDD = purrr::map_chr(shap, function(.shap) {
          purrr::pluck(.shap, "res") %>% 
            dplyr::filter(feature == "GDD") %>%
            dplyr::select(feature.value) %>%
            stringr::str_remove(".*=")})) %>%
        dplyr::mutate(fung = "Y") %>%
        dplyr::select(fung, phi, GDD) %>%
        # Convert from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
        dplyr::mutate(phi = phi*0.06725) %>%
        # Return (loss) on phi, given soybean price. In $/ha:
        dplyr::mutate(net.val = .price*phi) %>%
        # Net profit: substract cost of fungicide and application:
        dplyr::mutate(net.prof = net.val - .chemcost) 
      ,
      HQNF.shap %>% 
        dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
          purrr::pluck(.shap, "res") %>% 
            dplyr::filter(feature == "foliar.fungicide") %>%
            dplyr::pull(phi)})) %>% 
        dplyr::mutate(GDD = purrr::map_chr(shap, function(.shap) {
          purrr::pluck(.shap, "res") %>% 
            dplyr::filter(feature == "GDD") %>%
            dplyr::select(feature.value) %>%
            stringr::str_remove(".*=")})) %>%
        dplyr::mutate(fung = "N") %>%
        dplyr::select(fung, phi, GDD) %>%
        # Convert from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
        dplyr::mutate(phi = phi*0.06725) %>%
        # Return (loss) on phi, given soybean price. In $/ha:
        dplyr::mutate(net.val = .price*phi) %>%
        # Net profit: substract cost of fungicide and application:
        dplyr::mutate(net.prof = net.val - 0) 
      ) %>%
    dplyr::mutate(fung = factor(fung, levels = c("N", "Y"), labels = c("Unsprayed", "Sprayed"))) %>%
    dplyr::mutate(GDD = factor(GDD, levels = c("01", "02", "03", "04", "05")))
  
  hq.gdd %>%
    ggplot(., aes(x = GDD, y = net.prof, colour = GDD, shape = fung)) +
    coord_flip() +
    geom_jitter(position = position_jitter(seed = 2019, width = 0.1), size = 2, alpha = 0.25) +
    stat_summary(fun.y = "mean", geom = "point", size = 5) +
    ggsci::scale_color_uchicago(palette = "dark", drop = FALSE, alpha = 0.8) +
    theme_bw() +
    geom_hline(aes(yintercept = 0), color = "gray70", size = 0.6) +
    scale_y_continuous(limits = c(.ll, .ul), expand = c(0.005, 0.005)) +
    labs(x = .xlab, y = .ylab) +
    theme(
      legend.position = "none",
      axis.title.x = element_text(face = "bold", size = 13),
      axis.text.x  = element_text(size = 10, angle = 0),
      axis.title.y = element_text(size = 13, angle = 90, face = "bold"),
      axis.text.y  = element_text(size = 10),
      panel.grid = element_blank() ) +
    guides(colour = FALSE, shape = FALSE) +
    annotate("text", x = .ann.x, y = .ann.y, size = 2.5, color = "gray20", label = .pricelabel, hjust = 0) +
    ggtitle(.maintitle) +
    theme(plot.title = element_text(face = "bold", size = 12))
}  # end function roi.hq.gdd
```

### Single price point {.tabset .tabset-fade .tabset-pills}
* $576.30/tonne


#### Confidence intervals
```{r Econ-HQ-CI, eval=TRUE, echo=FALSE, results='markup'}
soy.price <- 576.30
chem.cost <- 61.90

hq.ci <-
    dplyr::bind_rows(
      HQF.shap %>% 
        dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
          purrr::pluck(.shap, "res") %>% 
            dplyr::filter(feature == "foliar.fungicide") %>%
            dplyr::pull(phi)})) %>% 
        dplyr::mutate(fung = "Y") %>%
        dplyr::select(fung, phi) %>%
        # Convert phi from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
        dplyr::mutate(phi = phi*0.06725) %>%
        # Return (loss) on phi, given soybean price. In $/ha:
        dplyr::mutate(net.val = soy.price*phi) %>%
        # Net profit: substract cost of fungicide and application:
        dplyr::mutate(net.prof = net.val - chem.cost) 
      ,
      HQNF.shap %>% 
        dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
          purrr::pluck(.shap, "res") %>% 
            dplyr::filter(feature == "foliar.fungicide") %>%
            dplyr::pull(phi)})) %>% 
        dplyr::mutate(fung = "N") %>%
        dplyr::select(fung, phi) %>%
        # Convert phi from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
        dplyr::mutate(phi = phi*0.06725) %>%
        # Return (loss) on phi, given soybean price. In $/ha:
        dplyr::mutate(net.val = soy.price*phi) %>%
        # Net profit: substract cost of fungicide and application:
        dplyr::mutate(net.prof = net.val - 0) 
      ) %>%
    dplyr::mutate(fung = factor(fung, levels = c("N", "Y"), labels = c("Unsprayed", "Sprayed")))


set.seed(14092)
groupwiseMean(net.prof ~ fung,
              data   = hq.ci,
              conf   = 0.95,
              digits = 4,
              R      = 10000,
              boot        = TRUE,
              traditional = FALSE,
              normal      = FALSE,
              basic       = FALSE,
              percentile  = FALSE,
              bca         = TRUE)
```


#### By MG
```{r Econ-HQ-MG-Original, eval=FALSE, echo=FALSE}
# Original, before revising into a function to be able to plot for different price points
soy.price <- 576.30
chem.cost <- 61.90

## By MG: All HQ fields, plot points by MG and fungicide use
hq.mg <-
  dplyr::bind_rows(
    HQF.shap %>% 
      dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "foliar.fungicide") %>%
          dplyr::pull(phi)})) %>% 
      dplyr::mutate(MG = purrr::map_chr(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "MG.f") %>%
          dplyr::select(feature.value) %>%
          stringr::str_remove("MG.f=")})) %>%
      dplyr::mutate(fung = "Y") %>%
      dplyr::select(fung, phi, MG) %>%
      # Convert phi from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
      dplyr::mutate(phi = phi*0.06725) %>%
      # Return (loss) on phi, given soybean price. In $/ha:
      dplyr::mutate(net.val = soy.price*phi) %>%
      # Net profit: substract cost of fungicide and application:
      dplyr::mutate(net.prof = net.val - chem.cost) 
    ,
    HQNF.shap %>% 
      dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "foliar.fungicide") %>%
          dplyr::pull(phi)})) %>% 
      dplyr::mutate(MG = purrr::map_chr(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "MG.f") %>%
          dplyr::select(feature.value) %>%
          stringr::str_remove("MG.f=")})) %>%
      dplyr::mutate(fung = "N") %>%
      dplyr::select(fung, phi, MG) %>%
      # Convert phi from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
      dplyr::mutate(phi = phi*0.06725) %>%
      # Return (loss) on phi, given soybean price. In $/ha:
      dplyr::mutate(net.val = soy.price*phi) %>%
      # Net profit: substract cost of fungicide and application:
      dplyr::mutate(net.prof = net.val - 0) 
    ) %>%
  dplyr::mutate(fung = factor(fung, levels = c("N", "Y"), labels = c("Unsprayed", "Sprayed"))) %>%
  dplyr::mutate(MG = factor(MG, levels = c("0", "I", "II", "III", "IV")))


# Plot ...
hq.mg %>%
  ggplot(., aes(x = MG, y = net.prof, colour = MG)) +
  coord_flip() +
  geom_jitter(position = position_jitter(seed = 2019, width = 0.1), size = 2, alpha = 0.25) +
  facet_wrap(~ fung, ncol = 2) +
  stat_summary(fun.y = "mean", geom = "point", size = 5) +
  # Based on RColorbrewer qualitative set 1:
  # scale_color_manual(values = c("#377eb8", "#ff7f00")) + 
  scale_color_brewer(type = "qual", palette = "Set1", direction = 1, drop = FALSE) +
  scale_y_continuous(limits = c(-150, 210), expand = c(0.005, 0.005)) +
  labs(x = "Maturity group", y = "Return ($/ha)") +
  theme_bw() +
  # geom_hline(aes(yintercept = 0), color = "gray70", size = 0.6) +
  theme(
    legend.position = "none",
    axis.title.x = element_text(face = "bold", size = 13),
    axis.text.x  = element_text(size = 10, angle = 0),
    axis.title.y = element_text(size = 13, angle = 90, face = "bold"),
    axis.text.y  = element_text(size = 10),
    panel.grid = element_blank(),
    # Bold the facet text labels:
    strip.text = element_text(face = "bold", size = 10)
    )
```

```{r Econ-HQ-MG-Single, eval=TRUE, echo=FALSE}
roi.hq.mg(.price = 576.30, .xlab = "Maturity group", .ylab = "Return ($/ha)", .pricelabel = "Price = $576.30/tonne")
```


#### By sowing date
```{r Econ-HQ-doy-Original, eval=FALSE, echo=FALSE}
## By doy
hq.doy <- 
  dplyr::bind_rows(
    HQF.shap %>% 
    dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
      purrr::pluck(.shap, "res") %>% 
        dplyr::filter(feature == "foliar.fungicide") %>%
        dplyr::pull(phi)})) %>% 
      dplyr::mutate(doy = purrr::map_dbl(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
        dplyr::filter(feature == "doy") %>%
        dplyr::select(feature.value) %>%
        stringr::str_remove(".*=") %>%
        as.numeric()})) %>%
      dplyr::mutate(fung = "Y") %>%
      dplyr::select(fung, phi, doy) %>%
      # Convert from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
      dplyr::mutate(phi = phi*0.06725) %>%
      # Return (loss) on phi, given soybean price. In $/ha:
      dplyr::mutate(net.val = soy.price*phi) %>%
      # Net profit: substract cost of fungicide and application:
      dplyr::mutate(net.prof = net.val - chem.cost)
    ,
    HQNF.shap %>% 
      dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "foliar.fungicide") %>%
          dplyr::pull(phi)})) %>% 
      dplyr::mutate(doy = purrr::map_dbl(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "doy") %>%
          dplyr::select(feature.value) %>%
          stringr::str_remove(".*=") %>%
          as.numeric()})) %>%
      dplyr::mutate(fung = "N") %>%
      dplyr::select(fung, phi, doy) %>%
      # Convert from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
      dplyr::mutate(phi = phi*0.06725) %>%
      # Return (loss) on phi, given soybean price. In $/ha:
      dplyr::mutate(net.val = soy.price*phi) %>%
      # Net profit: substract cost of fungicide and application:
      dplyr::mutate(net.prof = net.val - 0)
    ) %>%
  dplyr::mutate(fung = factor(fung, levels = c("N", "Y"), labels = c("Unsprayed", "Sprayed")))  

# Plot ...  
hq.doy %>%
  ggplot(., aes(x = net.prof, y = doy, colour = doy)) +
  geom_point(size = 2.0) +
  scale_colour_distiller(palette = "Spectral") +
  facet_wrap(~ fung, ncol = 2) +
  scale_x_continuous(limits = c(-150, 210), expand = c(0.005, 0.005)) +
  labs(x = "Return ($/ha)", y = "Sowing date") +
  theme_bw() +
  theme(axis.title.x = element_text(face = "bold", size = 13),
        axis.text.x  = element_text(size = 10, angle = 0),
        axis.title.y = element_text(face = "bold", size = 13, angle = 90),
        axis.text.y  = element_text(size = 10),
        # Bold the facet text labels:
        strip.text = element_text(face = "bold", size = 10)) +
  theme(legend.position = "right", legend.direction = "vertical", legend.box = "vertical") +
  labs(colour = "Sowing\ndate")
```

```{r Econ-HQ-doy-Single, eval=TRUE, echo=FALSE}
roi.hq.doy(.price = 576.30, .xlab = "Return ($/ha)", .ylab = "Sowing date")
```


#### By GDD
```{r Econ-HQ-GDD-Original, eval=FALSE, echo=FALSE}
## By GDD
hq.gdd <-
  dplyr::bind_rows(
    HQF.shap %>% 
      dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "foliar.fungicide") %>%
          dplyr::pull(phi)})) %>% 
      dplyr::mutate(GDD = purrr::map_chr(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "GDD") %>%
          dplyr::select(feature.value) %>%
          stringr::str_remove(".*=")})) %>%
      dplyr::mutate(fung = "Y") %>%
      dplyr::select(fung, phi, GDD) %>%
      # Convert from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
      dplyr::mutate(phi = phi*0.06725) %>%
      # Return (loss) on phi, given soybean price. In $/ha:
      dplyr::mutate(net.val = soy.price*phi) %>%
      # Net profit: substract cost of fungicide and application:
      dplyr::mutate(net.prof = net.val - chem.cost) 
    ,
    HQNF.shap %>% 
      dplyr::mutate(phi = purrr::map_dbl(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "foliar.fungicide") %>%
          dplyr::pull(phi)})) %>% 
      dplyr::mutate(GDD = purrr::map_chr(shap, function(.shap) {
        purrr::pluck(.shap, "res") %>% 
          dplyr::filter(feature == "GDD") %>%
          dplyr::select(feature.value) %>%
          stringr::str_remove(".*=")})) %>%
      dplyr::mutate(fung = "N") %>%
      dplyr::select(fung, phi, GDD) %>%
      # Convert from bu/acre to t/ha (1 bushel/acre = .06725 metric tonnes/ hectare):
      dplyr::mutate(phi = phi*0.06725) %>%
      # Return (loss) on phi, given soybean price. In $/ha:
      dplyr::mutate(net.val = soy.price*phi) %>%
      # Net profit: substract cost of fungicide and application:
      dplyr::mutate(net.prof = net.val - 0) 
    ) %>%
  dplyr::mutate(fung = factor(fung, levels = c("N", "Y"), labels = c("Unsprayed", "Sprayed"))) %>%
  dplyr::mutate(GDD = factor(GDD, levels = c("01", "02", "03", "04", "05"))) 

hq.gdd %>%
  ggplot(., aes(x = GDD, y = net.prof, colour = GDD)) +
  coord_flip() +
  geom_jitter(position = position_jitter(seed = 2019, width = 0.1), size = 2, alpha = 0.25) +
  facet_wrap(~ fung, ncol = 2) +
  stat_summary(fun.y = "mean", geom = "point", size = 5) +
  ggsci::scale_color_uchicago(palette = "dark", drop = FALSE, alpha = 0.8) +
  theme_bw() +
  scale_y_continuous(limits = c(-150, 210), expand = c(0.005, 0.005)) +
  labs(x = "GDD", y = "Return ($/ha)") +
  theme(
    legend.position = "none",
    axis.title.x = element_text(face = "bold", size = 13),
    axis.text.x  = element_text(size = 10, angle = 0),
    axis.title.y = element_text(size = 13, angle = 90, face = "bold"),
    axis.text.y  = element_text(size = 10),
    panel.grid = element_blank(),
    # Bold the facet text labels:
    strip.text = element_text(face = "bold", size = 10)
    )
```

```{r Econ-HQ-GDD-Single, eval=TRUE, echo=FALSE}
roi.hq.gdd(.price = 576.30, .xlab = "GDD", .ylab = "Return ($/ha)", .pricelabel = "Price = $576.30/tonne", .ann.x = 0.5)
```

### Multiple price points {.tabset .tabset-fade .tabset-pills}
#### By MG
<!-- Supplementary Figure S11 -->

```{r Econ-HQ-MG-Multiple, eval=TRUE, echo=FALSE, fig.height=8.0}
# Set width = 743, height = 650

p1 <- roi.hq.mg(.price = 350, .maintitle = "a", .pricelabel = "$350/tonne")
p2 <- roi.hq.mg(.price = 400, .maintitle = "b", .pricelabel = "$400/tonne")
p3 <- roi.hq.mg(.price = 450, .maintitle = "c", .pricelabel = "$450/tonne")
p4 <- roi.hq.mg(.price = 500, .maintitle = "d", .pricelabel = "$500/tonne")
p5 <- roi.hq.mg(.price = 550, .maintitle = "e", .pricelabel = "$550/tonne")
p6 <- roi.hq.mg(.price = 600, .maintitle = "f", .pricelabel = "$600/tonne")

grid.arrange(p1, p2, p3, p4, p5, p6, ncol = 2,
             left = grid::textGrob("Maturity group", 
                                     gp = grid::gpar(fontface = "bold", fontsize = 12), rot = 90),
             bottom = grid::textGrob("Return ($/ha)", 
                                     gp = grid::gpar(fontface = "bold", fontsize = 12))
             )
```


#### By GDD
```{r Econ-HQ-GDD-Multiple, eval=TRUE, echo=FALSE, fig.height=8.0}
p1 <- roi.hq.gdd(.price = 350, .maintitle = "a", .pricelabel = "$350/tonne", .ann.x = 0.6)
p2 <- roi.hq.gdd(.price = 400, .maintitle = "b", .pricelabel = "$400/tonne", .ann.x = 0.6)
p3 <- roi.hq.gdd(.price = 450, .maintitle = "c", .pricelabel = "$450/tonne", .ann.x = 0.6)
p4 <- roi.hq.gdd(.price = 500, .maintitle = "d", .pricelabel = "$500/tonne", .ann.x = 0.6)
p5 <- roi.hq.gdd(.price = 550, .maintitle = "e", .pricelabel = "$550/tonne", .ann.x = 0.6)
p6 <- roi.hq.gdd(.price = 600, .maintitle = "f", .pricelabel = "$600/tonne", .ann.x = 0.6)

grid.arrange(p1, p2, p3, p4, p5, p6, ncol = 2,
             bottom = grid::textGrob("Return ($/ha)", 
                                     gp = grid::gpar(fontface = "bold", fontsize = 12))
             )
```



# Computing environment
```{r SessionInfo}
# Last run on R version 3.5.3 (2019-03-11)
R.Version()$version.string
R.Version()$system
sessionInfo()
```
